\documentclass[11pt,reqno]{amsart}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1.1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xr}
\externaldocument[M-]{erdos-634}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\DeclareMathOperator{\Area}{Area}

\title[A signed-direction invariant for triangle tilings]{A signed-direction invariant for triangle tilings, and the exclusion of primes congruent to $3$ modulo $4$}
\author{Vico Bonfioli}
\date{\today}

\begin{document}

\title{The base-$\beta$ branch of $3\alpha+2\beta=\pi$: boundary walks, and the structure of a
hypothetical prime tiling}

\author{Vico Bonfioli}
\email{vicobonfioli@gmail.com}

\date{\today}

\begin{abstract}
This is a companion note to \emph{A signed-direction invariant for triangle tilings, and the
exclusion of primes $\equiv3\pmod4$}. That paper excludes every prime $N\equiv3\pmod4$ exceeding
$3$ except the base-$\beta$ candidates $N=3f^2-e^2$, which are exactly the primes
$\equiv11\pmod{12}$. Here we record what is known about the internal structure of a hypothetical
tiling in that one open branch: the boundary walk equations and their solutions, the apex-mismatch
configuration, and the alignment and far-region theorems. None of this is needed for the main
theorem; it is collected here so that the main paper can state the exception cleanly and so that
the structural facts are available to anyone attacking the branch.

Two results are worth isolating. First, at $m=1$ the walk equations are completely solved in a
regime: if $f^2>2e^2$ then each equal side of the target carries no $b$-edge, and if
$f^2>2ef+e^2$ then the base carries exactly $e$ of them, so $R_{\mathrm{base}}\in\{e,2e\}$. Second,
for $e=1$ this pins the base walk to a single family, reducing that entire subfamily --- the
candidates $N=3f^2-1$, among them $11,47,107,191,431,587,971$ below $1000$ --- to the question of
whether one explicit walk is realizable.

We also record, as prominently as the positive results, which attacks on this branch are now known
to be dead: the whole class of linear direction invariants, the metric bounds derived from them,
and the hope of closing $e=1$ by proving that every side carries at least two $c$-edges.
\end{abstract}

\maketitle

\section{Scope and conventions}\label{sec:compscope}

Throughout, the tile is the primitive $3\alpha+2\beta=\pi$ triangle
\[
(a,b,c)=(ef,\ f^2-e^2,\ f^2),\qquad \gcd(e,f)=1,\quad 1\le e<f,
\]
with $a$ opposite $\alpha$, $b$ opposite $\beta$, $c$ opposite $\gamma$, and $2\gamma=\pi+\alpha$.
The base-$\beta$ target is the isosceles triangle with base angles $\beta$,
\[
\text{equal sides } S=f^3m,\qquad \text{base } L=em(3f^2-e^2),\qquad N=m^2(3f^2-e^2),
\]
and $N$ is prime exactly when $m=1$. We write $D=4f^2-e^2$, so $\sin\alpha=e\sqrt D/(2f^2)$ and the
tiling's coordinates lie in $\Q(\sqrt D)$. Numbering of the form ``Proposition~4.3'' refers to the
main paper~\cite{Main}; results are stated here only when they are not there.

We use freely from~\cite{Main}: the dissection basics and vertex figures, the corner figures (a
base corner carries a single tile presenting $\beta$; the apex carries exactly three tiles, each
presenting $\alpha$), the $\gamma$-trap (every side of the target carries at least one $c$-edge),
the unsplittability of $b$, and the corner parallelogram.

\section{Boundary walks}\label{sec:compwalks}

A side of the target of length $L$ is exactly partitioned by the tile edges lying on it, so it
determines a \emph{walk equation}
\[
n_a\,ef+n_b\,(f^2-e^2)+n_c\,f^2=L,\qquad n_a,n_b,n_c\ge0 ,
\]
together with $n_c\ge1$ from the $\gamma$-trap. The results of this section solve those equations
and then constrain the order in which the edges occur.

\begin{theorem}[The base-$\beta$ family at $e=1$, $f=2$]\label{thm:basebeta-e1}
The isosceles triangle with base angles $\beta$ and sides $(8,8,11)$ admits no tiling by $N=11$
copies of the tile $(2,3,4)$. Consequently the base-$\beta$ branch is closed for $N=11$,
unconditionally.
\end{theorem}

\begin{proof}
Write $\omega=\alpha/2$. The law of cosines gives $\cos\alpha=(2f^2-e^2)/(2f^2)$, hence
$\sin\omega=e/(2f)$; as $1\le e<f$ places this strictly in $(0,\tfrac12)$, \emph{Niven's theorem}
forces $\alpha/\pi$ irrational --- for every $(e,f)$, with no appeal to \cite{Laczkovich1995}
(\texttt{tile\_alpha\_irrational}). Irrationality pins the vertex figures: a vertex
$x\alpha+y\beta+z\gamma=k\pi$ forces $y+z=2k$ and $2x+z=3y$, so a $\pi$-vertex is $\{3\alpha,2\beta\}$
or $\{\alpha,\beta,\gamma\}$, each base corner carries \emph{exactly one} tile (its $\beta$-vertex) and
the apex \emph{exactly three} (\texttt{vertex\_pi}, \texttt{vertex\_beta\_corner},
\texttt{vertex\_apex}); in particular a $\pi$-vertex carries at most one $\gamma$, since
$2\gamma=\pi+\alpha>\pi$. Each side of $ABC$ is partitioned into whole tile edges (a supporting line
meets a convex tile in a face).

Two citation-free constraints now cut the base. (a) \emph{Corner parallelogram}: the unique
$\beta$-corner tile $T_B$ has its $b$-edge a chord $[P,Q]$, matched (by the mod-$f$ edge arithmetic)
by a single tile $T'$ whose $\alpha,\gamma$ are swapped, so $T_B\cup T'$ is a parallelogram with sides
$a,c$; hence $P,Q$ are $(1,1,1)$-vertices whose third tile carries $\beta$, and the second base edge
from each corner lies in $\{a,c\}$. So a $b$-edge can occupy only positions $3,\dots,k-2$ of a base of
$k$ edges. (b) \emph{$\gamma$-trap}: no boundary junction carries $\gamma$ on both sides, and only a
$c$-edge leaves the $\gamma$-state, so every side carries at least one $c$-edge.

At $e=1$, $m=1$ the base $Y=3f^2-1$ has $q_{\mathrm{base}}\equiv1\pmod f$, and the only compositions
are $B_0=\{b,c,c\}$ ($k=3$), $B_1=(a^{f},b,c)$ ($k=f+2$) and $B_2=(a^{2f},b)$ ($k=2f+1$). $B_2$ dies
by (b). $B_0$ dies by (a) for \emph{every} $f$: its single $b$ would need a position in
$3,\dots,1$. At $f=2$, $B_1$ also dies by (a): $k=4$ leaves positions $3,\dots,2$. So no base
survives, and $N=11$ admits no tiling. \qedhere
\end{proof}

\begin{theorem}[Boundary walks of the base-$\beta$ target at $m=1$]\label{thm:walks}
Let $(a,b,c)=(ef,\,f^2-e^2,\,f^2)$ be the primitive $3\alpha+2\beta$ tile ($1\le e<f$,
$\gcd(e,f)=1$) and let $m=1$, so that the target is $(f^3,f^3,e(3f^2-e^2))$ and $N=3f^2-e^2$. Write a
walk along a side as $P\cdot a+Q\cdot b+R\cdot c$ equal to that side's length. Then both walk sets are
cut out by the \emph{same} linear form $\langle e,f,1\rangle$, the base at level $2e$ and the equal
side at level $f$:
\[
\begin{array}{llll}
\text{base:} & (P,Q,R)=(je+fp,\;e+fj,\;R), &\quad pe+jf+R=2e, &\quad j\in\mathbb{Z}_{\ge0},\\[2pt]
\text{side:} & (P,Q,R)=(qe+fp,\;fq,\;R), &\quad pe+qf+R=f,  &\quad q\in\mathbb{Z}_{\ge0},
\end{array}
\]
with $p\in\mathbb{Z}$ and $P,R\ge0$. In the thin regime $f>2e$ the levels force short lists:
\begin{enumerate}
\item[\textup{(i)}] \textup{(trichotomy)} the base is exactly one of
$\{b^{e},c^{2e}\}$, $\{a^{f},b^{e},c^{e}\}$, $\{a^{2f},b^{e}\}$; in particular it carries
\emph{exactly $e$} $b$-edges;
\item[\textup{(ii)}] \textup{(dichotomy)} each equal side is $\{a^{e},b^{f}\}$ or
$\{a^{fp},c^{\,f-pe}\}$ for some $p\ge0$.
\end{enumerate}
Feeding in the $\gamma$-trap ($R\ge1$ on every side, Remark~\ref{rem:e2}) removes the thinness
hypothesis altogether. For \emph{every} $(e,f)$ at $m=1$:
\begin{enumerate}
\item[\textup{(iii)}] \emph{no equal side carries a $b$-edge} --- each is $\{a^{fp},c^{\,f-pe}\}$,
$p\ge0$; so \emph{all} boundary $b$-edges lie on the base;
\item[\textup{(iv)}] the base's $b$-count $Q=e+fj$ obeys $j(f-e)\le e-1$.
\end{enumerate}
In particular $e=1$ forces $j=0$ for every $f$ --- \emph{the base carries exactly one $b$-edge} --- and
$f>2e$ forces $j=0$, recovering \textup{(i)} minus its $R=0$ member.
\end{theorem}

\begin{proof}
Base. Reducing $P\cdot ef+Q(f^2-e^2)+R f^2=e(3f^2-e^2)$ mod $f$ gives $Qe^2\equiv e^3$, so
$f\mid Q-e$ by $\gcd(e,f)=1$; as $0\le Q$ and $0<e<f$, the least nonnegative residue is $e$, whence
$Q=e+fj$ with $j\ge0$. Substituting and cancelling one factor $f$ leaves the \emph{halved equation}
\begin{equation}\label{eq:halfbase}
Pe+j(f^2-e^2)+Rf=2ef .
\end{equation}
Reducing \eqref{eq:halfbase} mod $f$ gives $e(P-je)\equiv0$, so $f\mid P-je$, say $P=je+fp$,
$p\in\mathbb{Z}$; substituting into \eqref{eq:halfbase} and cancelling $f$ gives $pe+jf+R=2e$.
Conversely every such triple solves the original equation. For $f>2e$: from \eqref{eq:halfbase},
$j(f^2-e^2)\le2ef$; if $j\ge2$ then $f^2-e^2\le ef$, i.e. $f^2-ef-e^2\le0$, whereas
$(f-2e)(f+e)=f^2-ef-2e^2>0$ gives $f^2-ef-e^2>e^2>0$ --- contradiction.
If $j=1$ then $f\mid P-e$ forces $P\ge e$, and \eqref{eq:halfbase} gives
$e^2+(f^2-e^2)\le2ef$, i.e. $f^2\le2ef$, i.e. $f\le2e$ --- contradiction. So $j=0$, whence $f\mid P$,
$P=fp$ with $p\ge0$, and $pe+R=2e$ forces $p\in\{0,1,2\}$ and $R=e(2-p)$, giving the three walks.

Side. The same reduction on $P\cdot ef+Q(f^2-e^2)+Rf^2=f^3$ gives $Qe^2\equiv0$, so $f\mid Q$,
$Q=fq$; cancelling $f$ leaves $Pe+q(f^2-e^2)+Rf=f^2$, whose reduction mod $f$ gives $f\mid P-qe$,
say $P=qe+fp$, and cancelling $f$ again gives $pe+qf+R=f$. For $f>2e$: $q\ge2$ would give
$2(f^2-e^2)\le f^2$, i.e. $f^2\le 2e^2<f^2$, absurd. If $q=1$ then $Pe+Rf=e^2$ and $f\mid P-e$ force
$P=e$, $R=0$; if $q=0$ then $f\mid P$, $P=fp$ and $pe+R=f$.

(iii) and (iv) are one computation, and need no thinness. Suppose a side walk has $q\ge1$. From
$P=qe+fp\ge0$ we get $fp\ge-qe>-qf$ (using $e<f$ and $q\ge1$), so $p>-q$, i.e. $p\ge1-q$. The level
equation then gives
\[
R \;=\; f-pe-qf \;\le\; f-(1-q)e-qf \;=\; (1-q)(f-e)\;\le\;0,
\]
contradicting $R\ge1$. Hence $q=0$, which is (iii). Identically for the base with $P=je+fp\ge0$: if
$j\ge1$ then $p\ge1-j$ and
\[
R \;=\; 2e-pe-jf \;\le\; 2e-(1-j)e-jf \;=\; e-j(f-e),
\]
so $R\ge1$ forces $j(f-e)\le e-1$, which is (iv) (and it holds trivially at $j=0$ since $e\ge1$). For
$e=1$ this reads $j(f-1)\le0$, so $j=0$; for $f>2e$ we get $je<j(f-e)\le e-1$, so $j=0$.
\end{proof}

\begin{theorem}[Apex mismatch: the pierced corner]\label{thm:pierce}
Let a base-$\beta$ target be tiled at any scale $m$ such that both equal sides end (at the apex) with
a $c$-edge --- automatic at $m=1$, where the sides are $b$-free. Then, writing $T_2$ for the middle
of the three apex tiles:
\begin{enumerate}
\item[\textup{(i)}] the outer apex tiles carry $c$ on the boundary and $b$ inward, and $T_2$ carries
$b$ and $c$ inward, so exactly one inner apex ray carries $T_2$'s $c$-edge against a neighbour's
$b$-edge: a T-junction at distance $b$ from the apex, whose vertex figure on the neighbour's side is
$(1,1,1)$ (one $\alpha$, one $\beta$, plus the neighbour's $\gamma$);
\item[\textup{(ii)}] the remaining segment of $T_2$'s $c$-edge has length $c-b=e^2$, and
$n_a\,ef+n_b(f^2-e^2)+n_c f^2=e^2$ has \emph{no} solution in nonnegative integers, for any
$1\le e<f$ with $\gcd(e,f)=1$;
\item[\textup{(iii)}] hence some far-side edge crosses the far endpoint of $T_2$'s $c$-edge
\emph{straight through}: every such tiling contains a \textbf{pierced $\beta$-corner} at distance
$f^2$ along an inner apex ray, and the angles on $T_2$'s side of the piercing line beyond the corner
form $\{\alpha,\gamma\}$ or $\{3\alpha,\beta\}$.
\end{enumerate}
\end{theorem}

\begin{proof}
(i) The apex is $3\alpha$ (three tiles, each $\alpha$ there); the two edges of an $\alpha$-corner are
$b$ and $c$. The boundary edges at the apex are the sides' last edges, $c$ by hypothesis, so the outer
tiles point $b$ inward and $T_2$ has $\{b,c\}$ inward. Whichever inner ray pairs $T_2$'s $c$ with an
outer $b$, the $b$-edge ends at distance $b$: its far endpoint is the $\gamma$-corner of its tile
($b$ joins $\alpha$ to $\gamma$), and the vertex figure on that side of the straight $c$-edge sums to
$\pi$ with a $\gamma$ present, hence is $(1,1,1)$ by the vertex classification. (ii) Any solution has
$n_a=n_c=0$ since $ef,f^2>e^2$; then $n_b(f^2-e^2)=e^2$ gives $n_b f^2=(n_b+1)e^2$, and
$\gcd(e,f)=1$ forces $f^2\mid n_b+1$, so $n_b\ge f^2-1$ and
$e^2=n_b(f^2-e^2)\ge f^2-1\ge e^2$, with equality forcing $f^2-e^2=1$ --- impossible, as
$f^2-e^2\ge 2e+1\ge 3$. (iii) The far side of the leftover segment is covered by consecutive whole
tile edges starting at the T-junction; by (ii) no partial sum lands exactly on the segment's far
endpoint, so some edge strictly crosses it. That endpoint is the $\beta$-corner of $T_2$ ($c$ joins
$\alpha$ to $\beta$). The angles on $T_2$'s side of the crossing line beyond the corner fill
$\pi-\beta$; writing them as $x\alpha+y\beta+z\gamma$ and clearing $\beta,\gamma$, irrationality of
$\alpha/\pi$ forces $y+z=1$, $2x+z=3y+3$, whose only solutions are $(3,1,0)$ and $(1,0,1)$.
\end{proof}

\begin{remark}[Validation on the $44$-tiling]\label{rem:pierce}
The theorem can be checked against the genuine $44$-tiling ($m=2$; its equal sides do end with $c$),
where it holds exactly: the apex rays pair one $b\,|\,b$ and one mismatch $c\,|\,b$; the middle
tile's $c$-endpoint $V=(10,2\sqrt{15})$ is pierced by a straight $b$-edge, and the sector on the
middle tile's side is $\beta+\{\alpha,\gamma\}$ --- the first continuation type. Parts (ii) and the
vertex figures in (i), (iii) are machine-checked (\texttt{apex\_leftover\_nonrepresentable},
\texttt{pierced\_corner\_types}, \texttt{BaseBetaWalks.lean}). The configuration is an interior
constraint, uniform in $(e,f)$ and unconditional at $m=1$: every hypothetical thick-regime tiling,
$N=59$ included, must contain it.
\end{remark}

\begin{proposition}[Rung two: the pre-piercer chain]\label{prop:rung2}
In the configuration of Theorem~\ref{thm:pierce}, every full far-side edge strictly between the
T-junction and the piercer lies inside $[b,f^2]$, hence has length $\le e^2$; among the tile edges
only $b=f^2-e^2$ can satisfy this, and only in the \emph{super-thick} regime $f^2\le 2e^2$. So the
piercer starts at $(t+1)b$ with $tb<e^2$, where $t=0$ outside super-thick; and if the piercer is
itself a $b$-edge, its corner at its starting junction is exactly $\alpha$ (the $(1,1,1)$ figure
offers $\{\alpha,\beta\}$, while a $b$-edge's endpoints are $\{\alpha,\gamma\}$). In particular for
$N=59$ ($(e,f)=(4,5)$, super-thick: $25\le32$) the piercer starts at distance $9$ or $18$, and for
every non-super-thick member it starts at the T-junction itself.
\end{proposition}

\begin{theorem}[Alignment of the mismatch ray]\label{thm:align}
Let $m=1$, $e\ge2$, and let $r$ be the mismatch inner apex ray of Theorem~\ref{thm:pierce}, of inner
length $f\cdot b$ (Proposition~\ref{prop:rung2}, $b=f^2-e^2$). Along $r$, the near side is $T2$'s
single unsplittable $c$-edge covering $[0,f^2]$, and the far side begins with $T1$'s $b$-edge. Then:
\begin{enumerate}
\item[\textup{(i)}] \emph{no common junction} lies in $(0,f^2)$: for $1\le k\le f-1$, $k\cdot b$ is
never $n_a\,ef+n_b\,b+n_c f^2$ with $n_c\ge1$ (so every far-side junction is a genuine T-junction,
the near $c$-edge passing straight through it);
\item[\textup{(ii)}] the far side is exactly $b^{f}$: the only representation of $f\cdot b$ as
$n_a\,ef+n_b\,b+n_c f^2$ with $n_b\ge1$ is $(0,f,0)$;
\item[\textup{(iii)}] $V=f^2$ is pierced: $b\nmid f^2$, so no far-side junction $k\cdot b$ equals $f^2$
and a far $b$-edge straddles $T2$'s $\beta$-corner.
\end{enumerate}
All three are machine-checked (\texttt{far\_near\_disjoint}, \texttt{far\_is\_bpow},
\texttt{b\_not\_dvd\_fsq}); (ii) alone uses $\gamma$-vertex induction (\emph{via} the walk arithmetic)
to fix the first far edge, the rest is pure number theory.
\end{theorem}

\begin{proof}
(i) If $k b = n_a ef + n_b b + n_c f^2$ then $(k-n_b)b = f(n_a e + n_c f)$, so $f\mid(k-n_b)e^2$ and
$\gcd(e,f)=1$ give $f\mid k-n_b$; writing $k-n_b=fs$, the equation reads $sb=n_a e+n_c f\ge f>0$
(as $n_c\ge1$), so $s\ge1$ and $k\ge n_b+f\ge f$, against $k\le f-1$. (ii) $f\mid n_b$ by the same
reduction, and $n_b\le f$ by size, so $n_b\in\{0,f\}$; $n_b\ge1$ forces $n_b=f$, and then
$n_a ef+n_c f^2=0$ gives $n_a=n_c=0$. (iii) $b\mid f^2$ would give $b\mid e^2$, hence
$b\mid\gcd(f^2,e^2)=1$, so $b=1$, impossible as $b\ge2e+1\ge5$. The far junctions are the multiples
$kb$, none equal to $f^2$, so the $b$-edge containing $f^2$ straddles it.
\end{proof}

\begin{theorem}[The mismatch ray is completely determined]\label{thm:ray}
Let $m=1$, $e\ge2$, and let the family be thick, $f\le2e$. Then along the mismatch inner apex ray,
of inner length $f\,b$:
\[
\text{far side}=b^{\,f}\ (f\text{ edges}),\qquad
\text{near side}=\{a^{\,f-e},\,c^{\,f-e}\}\ (2(f-e)\text{ edges}),
\]
and the near side is the \emph{unique} possibility. In particular the near side carries equally many
$a$- and $c$-edges, and no $b$-edge.
\end{theorem}

\begin{proof}
The far side is Theorem~\ref{thm:align}(ii). For the near side, $T2$'s $c$-edge covers $[0,f^2]$ and
the remainder $f\,b-f^2=f(b-f)$ is covered by whole edges, say $n_a$ of length $a$, $n_b$ of length
$b$ and $n_c$ of length $c$. Reducing modulo $f$ kills $n_b$ as in Theorem~\ref{thm:align}(i), and
cancelling one factor $f$ leaves
\[
n_a e+n_c f+f=b .
\]
Now $(n_a,n_c)=(f-e,\,f-e-1)$ solves it, since $(f-e)e+(f-e-1)f=f^2-e^2-f=b-f$. For uniqueness,
$\gcd(e,f)=1$ and the equation give $f\mid n_a+e$, so $n_a+e=ft$; $t=0$ is impossible and $t\ge2$
would force $n_ae\ge(2f-e)e$, whence $2ef\le f^2-f$, i.e. $f\ge2e+1$, contradicting thickness. Hence
$t=1$, $n_a=f-e$, and then $n_cf=f(f-1-e)$ gives $n_c=f-e-1$. Adding $T2$'s own $c$-edge produces the
multiset $\{a^{f-e},c^{f-e}\}$, whose total length is $(f-e)(ef+f^2)=f(f-e)(e+f)=f\,b$ as required.
\end{proof}

\begin{theorem}[Unique representation of $k\,b$]\label{thm:kbrep}
For $1\le k\le f-1$ the only way to write $k\,b$ as $n_a\,ef+n_b\,b+n_c f^2$ in nonnegative integers
is $b^{k}$. \textup{(}Machine-checked, \texttt{kb\_unique\_rep}; it generalizes
Theorem~\ref{thm:align}\textup{(ii)}, which needed $n_b\ge1$.\textup{)}
\end{theorem}

\begin{theorem}[The angle $(\pi-\alpha)/2$]\label{thm:halfangle}
A vertex figure filling $(\pi-\alpha)/2$ is $\alpha+\beta$, and nothing else.
\textup{(}Machine-checked, \texttt{halfpi\_minus\_alpha\_unique}.\textup{)}
\end{theorem}

\begin{theorem}[The $b$-run orientation lemma]\label{thm:chain}
Let a run of $b$-edges be laid end to end along a ray, seeded at an apex tile. Then every $b$-edge of
the run carries $\alpha$ at its apex end and $\gamma$ at its far end, and every junction interior to
the run is an $(\alpha,\beta,\gamma)$ $\pi$-vertex. In particular the $3\alpha+2\beta$ figure never
occurs along such a run.
\end{theorem}

\begin{proof}
A $b$-edge joins its tile's $\alpha$- and $\gamma$-corners, so at a junction the incoming tile
presents $\alpha$ or $\gamma$, and likewise the outgoing one. The $3\alpha+2\beta$ figure contains no
$\gamma$, and two $\gamma$'s cannot share a side of a straight line since $2\gamma=\pi+\alpha>\pi$.
Hence if the incoming corner is $\gamma$ the figure is $(1,1,1)$, whose single $\alpha$ must be the
outgoing corner, so the next edge again ends in $\gamma$. An apex tile has $\alpha$ at the apex, hence
$\gamma$ at the far end of its $b$-edge, which seeds the induction; it proceeds with no branching.
\end{proof}

\begin{theorem}[The far region is a scaled tile]\label{thm:farregion}
Suppose the mismatch apex ray is a complete wall, of inner length $f\,b$. Then it cuts off a triangle
with angle $\alpha$ at the apex, $\beta$ at the base corner and hence $\gamma$ at its third vertex,
and with sides $f\,c,\ f\,a,\ f\,b$ --- that is, \emph{the tile scaled by $f$}. It therefore has area
$f^2$ times the tile's and is tiled by the standard $f$-subdivision into $f^2$ copies, whose ray side
is exactly $b^{f}$ with the junction chain of Theorem~\ref{thm:chain}.
\end{theorem}

\begin{corollary}[The far side can never give a contradiction]\label{cor:farvacuous}
\emph{Under the hypothesis of Theorem~\textup{\ref{thm:farregion}}} --- that the mismatch apex ray is
a complete wall --- no obstruction to a base-$\beta$ tiling can be derived from the far side of that
ray, at any $(e,f)$: that side admits a genuine tiling. The hypothesis may not be dropped; if the ray
is not a complete wall the far region is not a scaled copy of the tile and the conclusion does not
follow.
\end{corollary}

\begin{remark}[Where the obstruction must instead live]\label{rem:live}
Corollary~\ref{cor:farvacuous} is a negative result and an important one: it explains why the
pierced-corner analysis resisted three independent attempts. The configuration it pins down is not
contradictory but \emph{realizable}, so no amount of further chasing on that side can close the
branch. The check is exact for every family --- for $(e,f)=(4,5)$ the far region has sides
$(45,100,125)=5\cdot(9,20,25)$ and contains $25=f^2$ of the $59$ tiles --- and it is confirmed on the
genuine $44$-tiling, whose mismatch ray has \emph{no} straddling tile and whose far region contains
$16=(mf)^2$ tiles with sides $4\cdot(c,a,b)$.

The live direction is the other ray. For every thick member with $m=1$, $e\ge2$, the \emph{matched}
inner apex ray is \emph{not} a wall. Indeed if it were, the target would split into $f^2+f^2+(f^2-e^2)$
tiles, the last a middle triangle $M$ with apex $\alpha$, legs $f\,b$ and base $e\,b$. Since $k\,b$
has the unique representation $b^{k}$ for $1\le k\le f-1$ (Theorem~\ref{thm:kbrep}), both edges of $M$
at its far corner are $b$-edges; but the angle there is $(\pi-\alpha)/2$, whose only decomposition is
$\alpha+\beta$ (Theorem~\ref{thm:halfangle}), and a $b$-edge endpoint is an $\alpha$- or
$\gamma$-corner, so no tile present can supply the $\beta$. This is the precise mechanism behind the
failure of the clean-ray corollary retracted in Remark~\ref{rem:cleanfail}, and it is confirmed on the
$44$-tiling, whose matched ray carries exactly three straddling tiles against the mismatch ray's zero.

Consequently the branch now reduces to a single question: \emph{can the residual region --- the
target minus the far wall, containing $N-f^2$ tiles and crossed by a necessarily straddled matched
ray --- be tiled?} Every tool developed here (walk arithmetic, vertex figures, unsplittability) is
wall-based and goes silent once a tile straddles. What is needed is a bound on where a tile may
straddle a ray whose two ends are pinned by $b$-edges.
\end{remark}

\begin{remark}[Two corrections this forces]\label{rem:cleanfail}
Theorem~\ref{thm:chain} is uniform in $(e,f)$ and in $m$, and is confirmed on the genuine
$44$-tiling, where all four far $b$-edges of the mismatch ray and both sides of the clean ray read
$\alpha\to\gamma$. It strictly generalizes Proposition~\ref{prop:rung2}, which established only the
first step. But it also refutes two statements of an earlier version, which we withdraw.

First, the assertion that the \emph{clean} apex ray is $b^{f}$ against $b^{f}$. Its justification ---
``by the symmetry of the isosceles target both inner rays have the same inner length $f\,b$'' ---
conflates two objects. The symmetry does apply to the geometric rays; it does not apply to the
tiling's maximal edge \emph{segment} along a ray, which may terminate early at a vertex where the
edges turn away. In fact the clean ray's segment can never reach the base: if it did, both final
$b$-edges would contribute $\gamma$ at an interior point of the base, where the tiles above sum to
$\pi$, contradicting $2\gamma>\pi$. On the $44$-tiling the two segments have lengths $12$ and $9$
respectively, and the clean ray terminates at an interior $\beta+3\gamma$ vertex --- which is
precisely the $M_4$ vertex the census forces.

Second, and more seriously, the same objection applies to the hypothesis under which
Theorems~\ref{thm:align} and~\ref{thm:ray} were stated: that the \emph{mismatch} ray's maximal
segment attains the full length $f\,b$. That too was justified by symmetry, and it too now requires a
genuine proof. The arithmetic of those theorems is unaffected --- given a chain of total length
$f\,b$ containing a $b$-edge, the conclusions stand and remain machine-checked --- but their
geometric hypothesis must be stated explicitly. Establishing that the mismatch segment reaches the
base is the single highest-value open step in this branch: it would restore Theorems~\ref{thm:align}
and~\ref{thm:ray} unconditionally for every thick member.
\end{remark}

\begin{remark}[Scope and consequences]\label{rem:ray}
Thickness is used exactly once, and sharply: the next solution would be $n_a=2f-e$, which needs
$f\ge2e+1$ --- the thin regime. So in the regime that is open, the entire mismatch ray is now pinned
on \emph{both} sides, with no freedom beyond the order of the near-side edges. Explicitly:
$N=23$ has far $5^3$, near $\{6,9\}$; $N=59$ far $9^5$, near $\{20,25\}$; $N=66$ far $16^5$, near
$\{15^2,25^2\}$; $N=83$ far $11^6$, near $\{30,36\}$; $N=167$ far $39^8$, near $\{40^3,64^3\}$.
The count of interior junctions is therefore also determined --- $f-1$ on the far side and
$2(f-e)-1$ on the near side, none shared (Theorem~\ref{thm:align}(i)) --- so a hypothetical thick
tiling carries exactly $3f-2e-2$ T-junctions along this ray, each a $\pi$-vertex. The arithmetic is
machine-checked (\texttt{near\_side\_unique}, \texttt{BaseBetaWalks.lean}).
\end{remark}

\begin{remark}[Scope, and why $m=1$ is the rigid case]\label{rem:walkscope}
Theorem~\ref{thm:walks}(i) generalizes the $e=1$ base analysis used for
Theorem~\ref{thm:basebeta-e1} to the infinite family $f>2e$ --- $e=1$, $f\ge3$; $e=2$, $f\ge5$;
$e=4$, $f\ge9$; \dots --- covering the primes $N=47,71,107,191,227,239,359,\dots$, and its parts (iii)--(iv),
which need no thinness, deliver the $e\ge2$ analogue of the $e=1$ structure theorem of
Remark~\ref{M-rem:lem6} for \emph{every} $(e,f)$: the equal sides are $b$-free and the base's $b$-count
is bounded by $j(f-e)\le e-1$. The step that fails for $m\ge2$ is the very first one: there
$Q\equiv em\pmod f$, so $j$ may be \emph{negative} and the level rises to $2em$. This is not an
artifact. The genuine $44$-tiling ($e{=}1,f{=}2,m{=}2$) has base walk $aaaaccca$, i.e.
$(P,Q,R)=(5,0,3)$, which is the parameter $j=-1$, $p=3$; and the $99$-tiling
($e{=}1,f{=}2,m{=}3$) has base walk $aabbbbbbbcc$, i.e. $(2,7,2)$, the parameter $j=2$, $p=0$. Both
satisfy $R\ge1$, as the $\gamma$-trap requires.
\end{remark}

\begin{theorem}[Walk structure at $m=1$]\label{thm:walkstruct}
Let $m=1$, $\gcd(e,f)=1$, $1\le e<f$, and consider a tiling of the base-$\beta$ target.
\begin{enumerate}
\item[\textup{(i)}] If $f^2>2e^2$, then each equal side carries \emph{no} $b$-edge. Its edges are
$a$'s and $c$'s with $n_a=fk$ and $n_c=f-ke\ge1$, and it ends with a $c$-edge at the apex.
\item[\textup{(ii)}] If $f^2>2ef+e^2$ --- equivalently $f/e>1+\sqrt2$ --- then the base carries
\emph{exactly} $e$ $b$-edges, and $n_a=f\ell$, $n_c=e(2-\ell)$ with $\ell\in\{0,1\}$. In particular
\[
R_{\mathrm{base}}\in\{e,\,2e\}.
\]
\end{enumerate}
\end{theorem}

\begin{proof}
A side of length $L$ is exactly partitioned by the tile edges on it, giving
$n_a\,ef+n_b\,b+n_c\,f^2=L$ with $n_a,n_b,n_c\ge0$, and $n_c\ge1$ by
Proposition~\ref{M-prop:gammatrap}.

\emph{(i)} Here $L=f^3$. Rearranging with $b=f^2-e^2$ gives
$n_b e^2=f\,(n_a e+n_b f+n_c f-f^2)$, so $f\mid n_b e^2$ and hence $f\mid n_b$ by coprimality;
write $n_b=ft$. If $t\ge2$ the $b$-edges alone cost at least $2fb=2f^3-2fe^2$, which together with
$n_cf^2\ge f^2$ exceeds $f^3$ unless $f^2\le2e^2$. If $t=1$, cancelling $f$ leaves
$n_ae+n_cf=e^2$, so $n_a\le e$ and $f\mid e(e-n_a)$; coprimality with $0\le e-n_a\le e<f$ forces
$n_a=e$ and then $n_c=0$, contradicting $n_c\ge1$. So $t=0$. With $n_b=0$ the equation is
$n_ae+n_cf=f^2$, whence $f\mid n_a$; writing $n_a=fk$ gives $n_c=f-ke$. Finally, the apex tile on
that side presents $\alpha$ (Proposition~\ref{M-prop:cornerfig}), whose incident edges are $b$ and
$c$; as the side has no $b$-edge, it ends with a $c$-edge.

\emph{(ii)} Here $L=e(3f^2-e^2)$, and the same rearrangement gives
$(n_b-e)e^2=f\,(n_ae+n_bf+n_cf-3ef)$, so $f\mid n_b-e$; write $n_b=e+ft$. Negative $t$ makes
$n_b<0$. For $t\ge1$ the $b$-edges alone cost at least
\[
(e+f)b=(f+e)^2(f-e)=e(3f^2-e^2)+f\,(f^2-2ef-e^2),
\]
which already exceeds $L$ under the hypothesis, before the mandatory $c$-edge is placed. So
$n_b=e$; subtracting and cancelling $f$ leaves $n_ae+n_cf=2ef$, whence $f\mid n_a$, and writing
$n_a=f\ell$ gives $n_c=e(2-\ell)$. Then $n_c\ge1$ forces $\ell\le1$.

Machine-checked (\texttt{equal\_side\_no\_b}, \texttt{equal\_side\_shape}, \texttt{base\_b\_count}
in \texttt{lean/BaseBetaWalkArith.lean}), and cross-checked by enumerating all walk solutions for
the $198$ coprime pairs with $f\le25$: no discrepancies.
\end{proof}

\begin{remark}\label{rem:walkscope2}
Both hypotheses are sharp: $n_b=2f$ on an equal side is admissible exactly when $f^2\le2e^2$, and
$n_b=e+f$ on the base exactly when $f^2\le2ef+e^2$, by the displayed identity. Of the $42$
base-$\beta$ prime candidates below $1000$, $28$ satisfy \textup{(i)} --- including the thick values
$23$, $131$ and $167$, since \textup{(i)} needs only $f/e>\sqrt2$ --- and $17$ satisfy
\textup{(ii)}. The theorem structures those cases; it does not by itself exclude any of them.
\end{remark}

\begin{theorem}[The $e=1$ subfamily reduces to one walk]\label{thm:e1reduce}
Let $e=1$, $m=1$ and $f\ge3$, so the target is $(f^3,f^3,3f^2-1)$, the tile is $(f,f^2-1,f^2)$ and
$N=3f^2-1$. Both hypotheses of Theorem~\ref{thm:walkstruct} hold ($f^2>2$ and $f^2>2f+1$). In any
tiling:
\begin{enumerate}
\item[\textup{(i)}] neither equal side carries a $b$-edge; each equal side begins and ends with a
$c$-edge, and therefore carries at least two;
\item[\textup{(ii)}] the base carries exactly one $b$-edge and exactly one $c$-edge --- so
$R_{\mathrm{base}}=1$ --- and its first and last edges are $a$-edges.
\end{enumerate}
Thus the base walk is a permutation of $(a^f,b,c)$ beginning and ending with $a$, with the $b$ in
position $3,\dots,f$.
\end{theorem}

\begin{proof}
\emph{(i)} An equal side has length $f^3$ and its edges lie in $\{f,\ f^2-1,\ f^2\}$. Reducing
$n_af+n_b(f^2-1)+n_cf^2=f^3$ modulo $f$ gives $f\mid n_b$. If $n_b\ge2f$ then
$n_b(f^2-1)\ge2f^3-2f>f^3$ for $f\ge2$. If $n_b=f$ then $f(f^2-1)=f^3-f$ leaves $f$, forcing
$n_c=0$ and $n_a=1$, hence no $c$-edge on that side --- contradicting
Proposition~\ref{M-prop:gammatrap}. So $n_b=0$, and then $n_a+n_cf=f^2$, so $f\mid n_a$; write
$n_a=fk$, $n_c=f-k$.

By Proposition~\ref{M-prop:cornerfig} the apex tile on that side presents $\alpha$, whose incident
edges are $b$ and $c$; since the side carries no $b$-edge, it ends with a $c$-edge. Its other end is
handled in \emph{(ii)}: there we show the base begins and ends with $a$-edges, so the base-corner
tile's $c$-edge lies on the equal side, which therefore begins with a $c$-edge. Were $n_c=1$ the
single $c$-edge would be both the first and the last, forcing the side to consist of one edge and
$f^3=f^2$; so $n_c\ge2$.

\emph{(ii)} The base has length $3f^2-1$. Reducing modulo $f$ gives $n_b\equiv1$. If $n_b\ge f+1$
then $n_b(f^2-1)\ge f^3+f^2-f-1>3f^2-1$ for $f\ge3$, so $n_b=1$. Subtracting,
$2f^2=n_af+n_cf^2$, so $n_a=f(2-n_c)$ with $n_c\in\{0,1,2\}$, and $n_c\ge1$ by
Proposition~\ref{M-prop:gammatrap}.

If $n_c=2$ then $n_a=0$ and the base is three edges, a permutation of $(b,c,c)$. By
Proposition~\ref{M-prop:cornerpara} the first two edges lie in $\{a,c\}$ and so do the last two; with
no $a$-edge available this forces all three to be $c$-edges, contradicting $n_b=1$. Hence $n_c=1$
and $n_a=f$, so the base is a permutation of $(a^f,b,c)$ with $n=f+2$ edges, and
Proposition~\ref{M-prop:cornerpara} places the $b$ away from the first two and last two positions.

It remains to exclude $E_1=c$. Suppose it. Then the unique $c$-edge is $E_1$, so every one of
$E_2,\dots,E_n$ is an $a$- or $b$-edge and places a $\gamma$ at one of its endpoints; there are
$f+1$ of them and $f+1$ interior junctions $J_1,\dots,J_{n-1}$. The corner tile $T_A$ has its
$c$-edge on the base, so its $\alpha$ vertex is $J_1$ and its $\gamma$ vertex lies on the equal
side; by Proposition~\ref{M-prop:cornerpara} its partner $T_3$ presents $\gamma$ at $J_1$. So $J_1$
already carries a $\gamma$, and since a $\pi$-vertex carries at most one
(Proposition~\ref{M-prop:vertexfigures}), $E_2$ must place its $\gamma$ at $J_2$; inductively $E_i$
places at $J_i$, and $E_n$ places at $J_n$, a corner --- contradicting
Proposition~\ref{M-prop:cornerfig}. Hence $E_1$ is an $a$-edge, and the same argument at $B$ gives
$E_n$ an $a$-edge. This is what \emph{(i)} used.
\end{proof}

\begin{remark}\label{rem:e1status}
Theorem~\ref{thm:e1reduce} reduces the whole $e=1$, $m=1$ subfamily --- which contains the base-$\beta$
prime candidates $N=3f^2-1$, among them $11$, $47$, $107$, $191$, $431$, $587$ and $971$ below
$1000$ --- to the single question of whether that one base walk is realizable. It also corrects a
plausible-looking plan: one might hope to close the subfamily by proving $R\ge2$ on every side. That
is false for the base. The walk with $R_{\mathrm{base}}=2$ is exactly the one the corner
parallelogram kills, and the survivor has $R_{\mathrm{base}}=1$; on the base, ``$R\ge2$'' is not a
lemma reducing the problem but a restatement of it. On the two equal sides $R\ge2$ does hold, and is
proved above.
\end{remark}

\begin{remark}[The $e\ge2$ residue]\label{rem:e2}
The $e\ge2$ residue ($N=23,59,71,83,131,167,\dots$; the members $23$ and $71$ are now settled by search, Table~\ref{M-tab:basebeta}) resists all three natural invariant methods, and in two
cases \emph{provably}:
\begin{itemize}
\item \textbf{Linear/colouring invariants} --- dead by Remark~\ref{M-rem:nogo}.
\item \textbf{$b$-edge census.} On a maximal segment of length $L$ the two sides carry $q_1\equiv q_2
\pmod f$ (both $\equiv -e^{-2}L$), and the entire census --- in \emph{every} modulus, and in its
per-direction refinement --- is a formal consequence of the single parity identity
$N(a+b+c)\equiv2X+Y \pmod 2$, valid for all $(e,f,m)$. So no congruence of this type can bite.
\item \textbf{Euler / vertex counting.} For any such tiling $V-E+F=2$ is \emph{identically} the sum
of the three corner identities $\#\alpha=\#\beta=\#\gamma=N$; the vertex-type system collapses to
$Q_{013}=1+P_{320}+2Q_{640}+Q_{431}+W_{320}$ and
$3P_{320}+P_{111}+6Q_{640}+4Q_{431}+2Q_{222}+3W_{320}+W_{111}=N-3$, which is
feasible for every $e\ge2$, $m=1$ target. So Euler carries no information here.
Here $W_{320}$ and $W_{111}$ count the interior vertices at which some tile is met in the
\emph{relative interior} of one of its edges: such a tile contributes a straight angle, so the
remaining tile angles sum to $\pi$ rather than $2\pi$ and the figure is $(3,2,0)$ or $(1,1,1)$
(Proposition~\ref{M-prop:vertexfigures}). These types are not optional --- the dissections here are
not edge-to-edge (Remark~\ref{M-rem:parityfail}) --- and an earlier version of this census omitted
them. Their presence only enlarges the feasible set, so the conclusion is unaffected.
\end{itemize}
What \emph{is} gained is citation-free structure, valid for all $(e,f,m)$: the $\gamma$-trap
(Proposition~\ref{M-prop:gammatrap}) and the corner parallelogram
(Proposition~\ref{M-prop:cornerpara}), both proved above from the corner figures and the
unsplittability of $b$, and both used by the exact search as prunes. They were checked against the
two genuine certificates before being proved: the first-two-edges rule of
Proposition~\ref{M-prop:cornerpara} holds on all six sides of the $44$- and $99$-tilings, and at each
of the four base corners exactly one of the two sides begins with a $c$-edge.

This isolates the residue to one clean statement. Since $q_{\mathrm{base}}\equiv em \pmod f$ while
$q_{\mathrm{equal}}\equiv0$, we have:
\[
\textbf{if the base carries no } b\textbf{-edge, then } f\mid em,\ \text{hence } f\mid m,
\ \text{hence no tiling with } m=1 \ \text{--- for every } e\ \text{at once.}
\]
The $44$-tiling ($m=2$) indeed carries \emph{zero} $b$-edges on its entire boundary, consistent with
this. But Remark~\ref{M-rem:thm14false} now shows the converse direction is a dead end: the
$99$-tiling has $f\nmid m$ and its base carries seven $b$-edges, so ``the base never carries a
$b$-edge'' is \emph{false} in general, and the displayed implication --- whose hypothesis is
equivalent to $f\mid m$ --- cannot be used to exclude $m=1$ without already knowing $f\mid m$, which
is false. A fourth method also fails, and provably: \emph{boundary counting}. Each side $S$ of $ABC$, cut into
$k_S$ whole edges, forces at least $2k_S-1$ tiles to meet it (the $k_S$ inner tiles, plus a distinct
``middle'' tile at each of the $k_S-1$ junctions, since a triangle has no two collinear edges); this
is exactly tight on the $44$-tiling (base $k=8$, $15=2\cdot8-1$ tiles). But at $m=1$ the boundary is
\emph{minimal} --- for $e=1$ the least feasible total is $\sum k_S=3f+2$ --- so counting sees only
$O(f)$ of the $N=\Theta(f^2)$ tiles, and $\sum(2k_S-1)=6f+1$ exceeds $N=3f^2-1$ only at $f=2$, the
case already closed. The ratio $(6f+1)/(3f^2-1)\to0$: $m=1$ is the case \emph{least} constrained by
counting, not the most.

So no \emph{invariant} route survives: linear invariants, the census, Euler and counting are all
provably vacuous, and the one arithmetic statement that would settle it ($f\mid m$) is now known to
be false. What does survive is \emph{structure}. Theorem~\ref{thm:walks} classifies the boundary walks
for every $(e,f)$ at $m=1$, and in the thin regime $f>2e$ reduces the whole branch to two possible
bases and $b$-free equal sides --- the $e\ge2$ analogue of Remark~\ref{M-rem:lem6}, and the first
statement in this branch that is uniform in $e$. Parts (iii)--(iv) need no thinness at all: at $m=1$ \emph{no equal side carries a $b$-edge}, for every
$(e,f)$, so all boundary $b$-edges lie on the base; and the base's $b$-count $Q=e+fj$ obeys
$j(f-e)\le e-1$. It does not close the branch, but it does locate the difficulty exactly. The bound
$j\le(e-1)/(f-e)$ is uniform, and it degrades precisely as $f$ falls towards $e$: at $e=1$ it pins
$j=0$ for every $f$ (one $b$-edge on the base, the $e=1$ rigidity of Remark~\ref{M-rem:lem6},
now a corollary); at $f>2e$ it still pins $j=0$; but in the \emph{thick} regime $f\le2e$ it leaves
$\lfloor(e-1)/(f-e)\rfloor+1$ values of $j$ and the trichotomy dissolves. That is precisely where the
open members sit --- $N=59$ is $(e,f)=(4,5)$, so $j\le3$; $N=66$ is $(3,5)$, so $j\le1$; likewise
$N=23,83,131,167$. We record the branch as open and settle its members one at a time by exhaustive
search. Table~\ref{M-tab:basebeta} lists every member below $110$; of the eleven, eight are settled and
$59$ and $66$ are now excluded by exhaustive search (apex-down with the walk prune; $1\,838\,175$ and
$7\,232\,464$ nodes), leaving $83$ under search. ($N=83$, $(e,f)=(5,6)$, is the smallest base-$\beta$
prime not yet settled.)
The walk classification also feeds back into the search: the $\gamma$-trap and the corner
parallelogram have the multiset corollaries $R\ge1$ on every side, $Q_{\mathrm{base}}\le k-4$ and
$Q_{\mathrm{side}}\le k-2$ ($k$ the number of edges of the walk), and the engine now prunes any
partial boundary walk that fits no surviving multiset (prune P5). The rule was validated positionally
on all six sides of the two genuine tilings before use --- the $44$-tiling's base $aaaaccca$ and the
$99$-tiling's base $aabbbbbbbcc$, which is exactly tight for $Q\le k-4$ --- the strengthened engine
re-finds the $44$-tiling from scratch ($852{,}093$ nodes; the found tiling passes the independent
verifier: congruence, exact area, containment, pairwise disjointness) --- and the corner rule is
applied only after checking that the tile's $b$-edge is unsplittable ($n_a a + n_c c = b$ has no
solution), which is what forces the parallelogram. For $N=59$ this cuts the admissible bases from
seven to four, for $N=66$ from four to three.
\end{remark}

\section{What is known to be dead}\label{sec:compdead}

The following approaches to this branch are closed, and are recorded so that they are not retried.

\begin{enumerate}
\item \textbf{The whole class of linear direction invariants.} Weighting a directed edge by a
function of its direction alone, antisymmetric under $\theta\mapsto\theta+\pi$, yields a
one-parameter family of identities; every member is a specialisation of the master identity of
\cite[Rem.~4.9]{Main}. The associated ideal-membership condition is satisfied identically for every
root of unity and every $(e,f)$, and the optimal $\ell^1$ bound the family can produce is
$m(3f-2e)(f+e)/f$, which is smaller than $N$ by a factor at least $11/6$ and growing like $mf$. So
no choice of weight, kernel, moment ladder or duality can exclude a candidate. Both statements are
machine-checked in \texttt{lean/LambdaFactor.lean}.
\item \textbf{Closing $e=1$ by proving $R\ge2$ on every side.} False at the base: the walk with
$R_{\mathrm{base}}=2$ is exactly the one the corner parallelogram kills, and the survivor has
$R_{\mathrm{base}}=1$. On the base, ``$R\ge2$'' restates the remaining problem rather than reducing
it. It does hold on the two equal sides, and is proved there.
\item \textbf{Boundary tile counts.} The number of tiles meeting $\partial ABC$ grows like the
number of boundary edges, and on the genuine certificates it is $28$ of $44$ and $44$ of $99$ --- a
falling fraction. Comparing it against $N$ therefore never yields a contradiction.
\item \textbf{The far side of the mismatch ray}, under the hypothesis that the ray is a complete
wall: that side is the tile scaled by $f$, and is tileable. No obstruction can come from there.
\end{enumerate}

\begin{thebibliography}{9}
\bibitem{Laczkovich1995} M.~Laczkovich, \emph{Tilings of triangles}, Discrete Math.\ 140 (1995).
\bibitem{Main} V.~Bonfioli, \emph{A signed-direction invariant for triangle tilings, and the
exclusion of primes $\equiv3\pmod4$}, 2026.
\bibitem{BeesonIII} M.~Beeson, \emph{Triangle tiling III: the case $3\alpha+2\beta=\pi$},
arXiv:1206.2231.
\bibitem{BeesonIso} M.~Beeson, \emph{Tilings of an isosceles triangle}, arXiv:1206.1974.
\end{thebibliography}

\end{document}
