\documentclass[11pt,reqno]{amsart}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1.1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\N}{\mathbb{N}}
\DeclareMathOperator{\Area}{Area}

\title[A signed-direction invariant for triangle tilings]{A signed-direction invariant for triangle tilings, and the exclusion of primes congruent to $3$ modulo $4$}
\author{Vico Bonfioli}
\date{\today}

\begin{document}

\begin{abstract}
For a triangle $T$ and a triangle $ABC$, an \emph{$N$-tiling} is a dissection of $ABC$ into $N$
triangles each congruent to $T$. Erd\H{o}s asked which $N$ occur; a folklore conjecture is that no
prime $N\equiv 3\pmod 4$ with $N>3$ does (the value $N=3$ occurs). By the classification of
Laczkovich and the branch theorems of Beeson, the conjecture reduces to a tile with a $2\pi/3$ angle
on a non-equilateral triangle, where a prime count forces $ABC$ isosceles. For that isosceles case
Beeson ruled out $N<36$ and explicitly left open whether $N$ can be prime (the smallest \emph{known}
tiling has $2673$ tiles); we settle it. We introduce a translation-invariant, signed-direction
tiling functional, linear in edge length and hence insensitive to non-edge-to-edge incidences, whose
integrality forces, for an isosceles target, that $(c-a-b)/\sqrt b$ be an integer for a primitive
triple with $c^2=a^2+ab+b^2$; an elementary lemma shows this never occurs. With a self-contained
reduction of the scalene shapes, this completes the exclusion of primes $\equiv 3\pmod 4$ exceeding
$3$, conditional on the cited classification of the remaining branches. Consequently the prime case
of the full problem is complete: a prime $p$ occurs if and only if $p=2$, $p=3$, or
$p\equiv1\pmod4$. Beyond primes, we determine the admissible spectrum of each sporadic $2\pi/3$
branch --- for the isosceles target, writing $b=de^2$ with $d$ squarefree, every count has the form
$N=dw^2(a+2b)$ with $e\mid w(c-a-b)$ --- bounding the realizable set from outside; and a
spectrum theorem shows that the counts passing all invariant conditions on the isosceles and
$F_1$ targets are \emph{exactly} Zhang's constructed families, closing the necessary side of
those branches; the equilateral criteria likewise reduce to elementary divisor conditions. Combining the spectra with the published
branch theorems and an exhaustive exact search of the surviving finite instances, we settle every
previously undetermined value up to $43$: no triangle can be cut into $14$, $15$, $21$, $22$, $30$,
$33$, $35$, $38$, $39$, or $42$ congruent triangles; $N=46$, previously the sharpest test of Zhang's
completeness conjecture, is likewise excluded; and membership in the tile-count set is shown to be
decidable. The arithmetic and combinatorial layer is
machine-checked in Lean~4 with Mathlib.
\end{abstract}

\maketitle

\section{Introduction}

Let $T$ be a triangle (the \emph{tile}). An \emph{$N$-tiling} of a triangle $ABC$ is a way of
writing $ABC$ as a union of $N$ triangles, each congruent to $T$, with pairwise disjoint interiors.
We do \emph{not} assume the tiling is edge-to-edge: a vertex of one tile may lie in the relative
interior of an edge of another. Erd\H{o}s asked (reported by Soifer~\cite{Soifer}) to determine the
set of $N$ for which some triangle admits an $N$-tiling by some tile. Every perfect square occurs
(any triangle, by the $n^2$ subdivision), and Soifer observed that $n^2+m^2$, $2n^2$, $3n^2$ and
$6n^2$ occur as well; in particular $3=3\cdot 1^2$ occurs. The outstanding question is whether the
primes $\equiv 3\pmod 4$ that exceed $3$, which are exactly the odd primes that are neither sums of
two squares nor of the form $3n^2$, are excluded.

\begin{theorem}\label{thm:main}
No prime $N\equiv 3\pmod 4$ with $N>3$ is a number of congruent triangles into which some triangle
can be cut. In particular, no triangle can be cut into $19$ congruent triangles.
\end{theorem}

\noindent The restriction $N>3$ is necessary: an equilateral triangle joined to its centre splits
into $3$ congruent triangles, so $N=3$ occurs.

The proof rests on Laczkovich's classification of triangle tilings~\cite{Laczkovich1995,
Laczkovich2012}, organized by Beeson across a series of papers \cite{BeesonI, BeesonIII,
BeesonIso, BeesonSeven, BeesonEq}. For a prime number of tiles every branch of the classification
is excluded by an existing theorem, with one exception: a tile having a $2\pi/3$ angle, tiling a
non-equilateral triangle. We treat that branch.

This branch is the active frontier. Zhang~\cite{Zhang} classifies the non-equilateral
$2\pi/3$ shapes into six sporadic similarity types (Section~\ref{sub:shapes} below), constructs
families of tilings for each, and conjectures that the constructed $N$, all composite, are the only
ones; the present results prove the no-prime half of that conjecture for the isosceles type, and
reduce the scalene types directly. For the isosceles type Beeson~\cite{BeesonIso} proved that no
tiling exists with $N<36$ and \emph{explicitly left open whether $N$ can be prime}; the smallest
tiling presently known has $2673$ tiles (Herdt, reported in~\cite{BeesonIso}). The invariant below
settles the question, excluding \emph{every} prime. The adjacent Erd\H{o}s Problem~633, on tilings
into a square number of triangles, was recently settled by Beeson, Laczkovich and
Zhang~\cite{Erdos633}.

Two reductions prepare it. First, by the rationality theorem of Beeson and
Zhang~\cite{BeesonZhang}, such a tile has commensurable sides, so after scaling we may take it
integer-sided with $c^2=a^2+ab+b^2$. Second, an elementary area-and-incidence argument shows that a
\emph{prime} number of such tiles forces $ABC$ to be \emph{isosceles}
(Section~\ref{sec:reduction}).

The heart of the paper is Section~\ref{sec:invariant}. The natural parity argument for a $2\pi/3$
tile (a black/white colouring of the tiles) fails, because a vertex of the tiling may be surrounded
by an even number of tiles, so no consistent two-colouring exists. We replace it by a functional
$\Phi$ that assigns to a directed edge of direction $\theta=j\frac\pi3+k\alpha$ the weight
$(\text{length})\cdot(-1)^j$. Two features make it work: $\Phi(\theta+\pi)=-\Phi(\theta)$, so
interior edges cancel; and the weight is \emph{linear in edge length}, so the cancellation is
unaffected by non-edge-to-edge incidences, where one long edge meets several shorter ones summing
to it. Summing over the tiles, $\Phi$ of the boundary equals an integer multiple of a fixed
tile-value $c+a-b$. For an isosceles target this forces $(c-a-b)/\sqrt b\in\Z$, which never holds
(Section~\ref{sec:isosceles}). Assembling the branches proves Theorem~\ref{thm:main}
(Section~\ref{sec:assembly}).

The combinatorial claims are verified by the scripts in the accompanying repository, and the entire
arithmetic layer, including Lemma~\ref{lem:nonint} and the reduction of Section~\ref{sec:reduction},
is formalized and machine-checked in Lean~4 with Mathlib; see Section~\ref{sec:verification}.

\section{Preliminaries}\label{sec:prelim}

\subsection*{The classification.}
Fix a prime $N=p>3$ with $p\equiv 3\pmod 4$. By Laczkovich~\cite{Laczkovich1995,Laczkovich2012},
every $N$-tiling of a triangle falls into one of finitely many types of pairs $(ABC,T)$. The
relevant dichotomy, in Beeson's organization~\cite{BeesonSeven}, is: either the angles of $T$ are
pairwise commensurable with $\pi$, or they are not. If they are commensurable, then $N$ is a square,
a sum of two squares, or $2$, $3$ or $6$ times a square \cite[Thm.~3 and Table~3]{BeesonSeven}; but
$p>3$ with $p\equiv3\pmod4$ is a square only if $p$ is one (it is not), a sum of two squares only if
$p\not\equiv3\pmod4$, and $2n^2,3n^2,6n^2$ only if $p$ is even or $3\mid p$ (here $p$ is odd and
$p>3$), so $p$ is none of these (it is precisely for $p=3=3\cdot1^2$ that this step would fail).
If the angles are not commensurable, then, after the right-angle and similar-tile cases, which give
$N$ a sum of two squares or $N=n^2$ \cite{BeesonI, SWW}, the tile has a special angle and falls into
one of: $3\alpha+2\beta=\pi$, for which $N$ is not prime \cite{BeesonIII}; an isosceles tile with
$\gamma=2\alpha$, for which $N$ is not squarefree \cite[Thm.~11.7]{BeesonIso}; or the tile has an
angle equal to $\pi/3$ or $2\pi/3$. The case of a $\pi/3$ or $2\pi/3$ tile on an \emph{equilateral}
triangle gives $N$ not prime \cite{BeesonEq}. What remains for a prime $N$ is a tile with a $\pi/3$
or $2\pi/3$ angle on a \emph{non-equilateral} triangle. The vertex enumeration of
Section~\ref{sub:shapes} shows the $\pi/3$ case admits only equilateral or tile-similar $ABC$,
already covered; so the sole remaining branch is a $2\pi/3$ tile, which we now fix.

\subsection*{The tile.}
Throughout, $T$ has angles $(\alpha,\beta,\gamma)$ opposite sides $(a,b,c)$, with
$\gamma=2\pi/3$, hence $\alpha+\beta=\pi/3$; we treat the incommensurable case, $\alpha$ an
irrational multiple of $\pi$. By Beeson--Zhang~\cite{BeesonZhang}, $T$ has commensurable sides, so
we scale to
\begin{equation}\label{eq:tile}
(a,b,c)\in\Z^3,\qquad \gcd(a,b,c)=1,\qquad c^2=a^2+ab+b^2
\end{equation}
(the law of cosines at $\gamma=2\pi/3$). We call such a triple a \emph{primitive $120^\circ$-triple}.
If a prime $p$ divides two of $a,b,c$ it divides the third (by~\eqref{eq:tile}), so
\eqref{eq:tile} gives $\gcd(a,b)=\gcd(a,c)=\gcd(b,c)=1$. One computes
\begin{equation}\label{eq:trig}
\sin\alpha=\tfrac{a\sqrt3}{2c},\quad \cos\alpha=\tfrac{2b+a}{2c},\qquad
\sin\beta=\tfrac{b\sqrt3}{2c},\quad \cos\beta=\tfrac{2a+b}{2c}.
\end{equation}

\subsection*{The direction grid.}
Set $G=\{\,j\frac\pi3+k\alpha:j,k\in\Z\,\}$ (mod $2\pi$). We claim every edge of every tile in a
tiling points in a direction lying in $G$, for a single fixed reference. Fix the reference along an
edge of one tile; its three edge-directions are then in $G$, since the tile angles
$\alpha,\beta=\frac\pi3-\alpha,\gamma=\frac{2\pi}3$ all lie in $\Z\alpha+\Z\frac\pi3$. Now argue by
adjacency. The tiling fills a connected region, so any tile $t'$ shares at least a boundary point
$P$ with the union of the tiles already placed; at $P$ the surrounding corner angles each belong to
$\{\alpha,\beta,\gamma\}$, and a directed edge of $t'$ at $P$ differs from a known grid direction at
$P$ by a sum of such angles, hence lies in $G$; the remaining edges of $t'$ then differ from it by
$\Z$-combinations of $\alpha,\frac\pi3$, so all of $t'$ is in $G$. This uses only the angles meeting
at a point and so applies verbatim at non-edge-to-edge incidences, where $P$ lies in the relative
interior of an edge (the angles there sum to $\pi$ rather than $2\pi$). Since $\alpha/\pi$ is
irrational, $\frac\pi3$ and $\alpha$ are $\Q$-linearly independent, so the pair $(j,k)$ is
determined by the direction (and $(-1)^j$ by the direction alone, as $2\pi=6\cdot\frac\pi3$).

\subsection*{Vertex types and shapes of $ABC$.}\label{sub:shapes}
A corner of $ABC$ is filled by tile-corners: if $P,Q,R\ge0$ (not all $0$) of them are
$\alpha$-, $\beta$-, $\gamma$-corners, the corner measures
$P\alpha+Q\beta+R\gamma=(P-Q)\alpha+(Q+2R)\tfrac\pi3$. Write $(m,k):=(P-Q,\,Q+2R)$. Since $Q\equiv k
\pmod2$, $0\le Q\le k$, and $P=m+Q\ge0$, the pair $(m,k)$ is \emph{realizable} exactly when
\begin{equation}\label{eq:realizable}
k\ge1\ \text{and}\ m\ge -k,\qquad\text{or}\qquad k=0\ \text{and}\ m\ge1.
\end{equation}
The three corners of $ABC$ have angles $m_i\alpha+k_i\frac\pi3$ summing to $\pi=3\cdot\frac\pi3$;
as $\alpha$ is irrational this forces
\begin{equation}\label{eq:cornersum}
\textstyle\sum_i m_i=0,\qquad \sum_i k_i=3 .
\end{equation}
By~\eqref{eq:realizable} each $m_i+k_i\ge0$, and by~\eqref{eq:cornersum} $\sum_i(m_i+k_i)=3$; hence
each $m_i+k_i\in\{0,1,2,3\}$ and $m_i\in[-k_i,\,3-k_i]\subseteq[-3,3]$. The enumeration is therefore
finite and \emph{independent of} $\alpha$. Checking the finitely many triples
$\{(m_i,k_i)\}$ satisfying \eqref{eq:realizable}, \eqref{eq:cornersum} and $0<m_i\alpha+k_i\frac\pi3
<\pi$ (done in exact arithmetic in Section~\ref{sec:verification}) leaves exactly eleven shapes of
$ABC$: the equilateral triangle; two isosceles triangles, with base angles $\alpha$
(apex $\alpha+3\beta$) and $\beta$ (apex $\beta+3\alpha$); and eight scalene triangles, namely
\[
F_1=(\alpha,\alpha+\beta,\alpha+2\beta),\ \ F_2=(2\alpha,2\beta,\alpha+\beta),\ \
F_3=(\alpha,2\alpha,3\beta),\ \ F_4=(\alpha,2\beta,2\alpha+\beta),
\]
their reflections under $\alpha\leftrightarrow\beta$ (with $F_2$ self-paired), and the tile-similar
triangle $(\alpha,\beta,2\pi/3)$. Since $\alpha/\pi$ is irrational, distinct pairs $(m,k)$ give
distinct angles, so the labels \emph{equilateral}, \emph{isosceles}, \emph{scalene} attached to
these types are unambiguous: no accidental coincidence of angles can occur, as any such coincidence
would force $\alpha\in\Q\pi$. These types coincide with the six sporadic non-equilateral $2\pi/3$
similarity types of Zhang~\cite{Zhang}.

\subsection*{The area identity.}
If $ABC$ is similar to a fixed shape whose primitive integer side-proportion vector is $D$
($\gcd$ of its entries $1$), and $ABC$ is $N$-tiled, then each side of $ABC$ is a disjoint union of
whole tile-edges (a tile meeting a straight portion of the boundary has a whole side on it), hence
an integer; so the sides of $ABC$ are $k\cdot D$ for an integer $k\ge1$, and
\begin{equation}\label{eq:area}
N=\frac{\Area(ABC)}{\Area(T)}=k^2N_0,\qquad N_0:=\frac{\Area(D)}{\Area(T)},\qquad
\Area(T)=\tfrac{\sqrt3}{4}ab .
\end{equation}
This is a necessary condition on $N$.

\section{Reduction to the isosceles case}\label{sec:reduction}

\begin{proposition}\label{prop:reduction}
Let $T$ be a tile with angles $(\alpha,\beta,2\pi/3)$, $\alpha/\pi$ irrational. If $T$ $N$-tiles a
triangle and $N$ is prime, then $ABC$ is isosceles and not equilateral.
\end{proposition}

\begin{proof}
By Section~\ref{sub:shapes}, the corner-type triple of $ABC$ is the equilateral one, the
tile-similar one, one of $F_1,\dots,F_4$ or their reflections, or one of the two isosceles ones.
The equilateral case gives $N$ not prime \cite[Thm.~6]{BeesonEq}; the tile-similar case gives
$N=n^2$ \cite{BeesonI, SWW}, not prime. For the remaining non-isosceles shapes we compute $N_0$
from \eqref{eq:area}; in each case $N=k^2N_0$ is composite.

\emph{$F_2$ and $F_4$.} The side-proportion vector of $F_2$ is
$\bigl(a(a+2b),\,b(2a+b),\,c^2\bigr)$ with the $\pi/3$ vertex between the first two sides, giving
$N_0=(a+2b)(2a+b)$. For $F_4$ one checks the side-vector $\bigl(ac,\,b(2a+b),\,(a+b)c\bigr)$ has
$\gcd 1$ (any common prime $g$ divides $c$ and then $g^2\mid 3b^2$, forcing $g=1$), giving
$N_0=(a+b)(2a+b)$. Both are products of two integer factors each at least $3$, hence composite, so
$N=k^2N_0$ is composite.

\emph{$F_3$.} The law of sines gives the side-proportion vector
$\bigl(ac^2,\,a(a+2b)c,\,3ab(a+b)\bigr)$, whose entries share the factor $a$; dividing it out leaves
$\bigl(c^2,\,(a+2b)c,\,3b(a+b)\bigr)$, and $N_0=3(a+b)(a+2b)$. This is divisible by $3$, hence
composite, so $N\equiv0\pmod3$ is composite.

\emph{$F_1$.} The side-vector is $(a,c,a+b)$ with the $\pi/3$ vertex between the sides $a$ and
$a+b$, so $N_0=(a+b)/b$ and $N=k^2(a+b)/b$. As $\gcd(b,a+b)=1$, integrality forces $b\mid k^2$, so
$N=t(a+b)$ with $t=k^2/b\in\Z_{\ge1}$. It remains to show $a+b$ is composite. Suppose $a+b=p$ is
prime. Since $(a+b)^2-c^2=ab$ by~\eqref{eq:tile}, we have $ab=p^2-c^2$, so $a,b$ are the roots of
$x^2-px+(p^2-c^2)$, whose discriminant $4c^2-3p^2$ must be a perfect square $d^2$; then
$3p^2=(2c-d)(2c+d)$. With $2c-d<2c+d$ the factorizations of $3p^2$ into two positive factors are
$(1,3p^2)$, $(3,p^2)$, $(p,3p)$, and in each the smaller root $\tfrac{p-d}{2}$ is not a positive
integer: in the first, $d=(3p^2-1)/2>p$, so the root is negative; in the second, $d=(p^2-3)/2$ and
the root $\tfrac{p-d}{2}=-\tfrac{(p-3)(p+1)}{4}$ is negative for $p>3$; in the third, $d=p$ gives
$c=p$ and $ab=p^2-c^2=0$. (The case $p\le3$ is impossible since $a+b\ge8$ for a primitive
$120^\circ$-triple.) Hence $a+b\ge8$ is composite, and $N=t(a+b)$ is composite.

The reflected shapes are handled by $\alpha\leftrightarrow\beta$ (which swaps $a\leftrightarrow b$
and leaves each $N_0$ above of the same form). So a prime $N$ forces the corner-type triple of
$ABC$ to be one of the two isosceles types; those have angles $(\varphi,\varphi,\pi-2\varphi)$ with
$\varphi\in\{\alpha,\beta\}$, and they are never equilateral ($\varphi=\frac\pi3$ would force
$\beta=0$ or $\alpha=0$). Hence $ABC$ is isosceles and not equilateral.
\end{proof}

\section{The signed-direction invariant}\label{sec:invariant}

Fix the reference so the direction grid is $G=\{\,j\frac\pi3+k\alpha\,\}$. Because
$\beta=\frac\pi3-\alpha$, every grid direction also has the form $(j+k)\frac\pi3-k\beta$, so we may
read off the coefficient of $\frac\pi3$ in two coordinate systems. Define, for a direction
$\theta\in G$,
\[
f_\alpha(\theta)=(-1)^{j}\ \ (\theta=j\tfrac\pi3+k\alpha),\qquad
f_\beta(\theta)=(-1)^{j'}\ \ (\theta=j'\tfrac\pi3+k'\beta).
\]
Both are well defined (Section~\ref{sec:prelim}), and both satisfy
\begin{equation}\label{eq:antisym}
f(\theta+\pi)=-f(\theta),
\end{equation}
since adding $\pi=3\cdot\frac\pi3$ increases the $\frac\pi3$-coefficient by $3$. They are genuinely
different functions: $f_\beta=(-1)^{k}f_\alpha$.

For $f\in\{f_\alpha,f_\beta\}$ and a directed edge of length $L$ and direction $\theta$, assign the
weight $L\,f(\theta)$. For a tile $t$ with boundary traversed counterclockwise, put
$C_f(t)=\sum_{\text{edges}}L\,f(\theta)$, and for the boundary of $ABC$ put
$\Phi_f(\partial ABC)=\sum_{\text{sides}}L\,f(\theta)$ (counterclockwise).

\begin{lemma}[Cancellation]\label{lem:cancel}
For each $f\in\{f_\alpha,f_\beta\}$, $\displaystyle\sum_{\text{tiles}}C_f(t)=\Phi_f(\partial ABC)$.
\end{lemma}

\begin{proof}
For a grid direction $\theta$ let $\Lambda(\theta)$ be the total length of all directed tile-edges
of direction $\theta$, summed over every tile (counterclockwise) and every edge; then, grouping the
double sum $\sum_t C_f(t)$ by direction,
\begin{equation}\label{eq:lambda}
\sum_{\text{tiles}}C_f(t)=\sum_{\theta}\Lambda(\theta)\,f(\theta).
\end{equation}
Split each tile-edge into its maximal sub-segments that are either interior to $ABC$ or contained in
$\partial ABC$; this only refines the sums and changes nothing. Consider the finite set of maximal
straight segments $S$ carved out on the tiling's edges. If $S$ lies in the interior of $ABC$, a
neighbourhood of a generic point of $S$ is a disc split by $S$ into two half-discs, each tiled; the
tiles on one side meet $S$ in directed edges of total length $|S|$ pointing one way, say $\theta$,
and those on the other side in directed edges of total length $|S|$ pointing $\theta+\pi$ (the two
subdivisions may differ, a non-edge-to-edge incidence, but each side covers $S$ exactly once because
the tiles cover $ABC$ with disjoint interiors). If instead $S\subseteq\partial ABC$, only the single
tile inside $ABC$ meets it, contributing length $|S|$ in the counterclockwise direction of
$\partial ABC$. Writing $\Lambda=\Lambda_{\mathrm{int}}+\Lambda_{\mathrm{bd}}$ accordingly,
interior segments give $\Lambda_{\mathrm{int}}(\theta)=\Lambda_{\mathrm{int}}(\theta+\pi)$ for every
$\theta$, while $\Lambda_{\mathrm{bd}}(\theta)$ is the counterclockwise boundary length in direction
$\theta$. Substituting into~\eqref{eq:lambda} and pairing $\theta$ with $\theta+\pi$,
\[
\sum_{\{\theta,\theta+\pi\}}\Lambda_{\mathrm{int}}(\theta)\bigl(f(\theta)+f(\theta+\pi)\bigr)=0
\]
by~\eqref{eq:antisym}, so $\sum_{\text{tiles}}C_f(t)=\sum_\theta\Lambda_{\mathrm{bd}}(\theta)f(\theta)
=\Phi_f(\partial ABC)$.
\end{proof}

\begin{lemma}[Tile value]\label{lem:value}
For every placement of $T$, $C_{f_\alpha}(t)=\pm(c+a-b)$ and $C_{f_\beta}(t)=\pm(c+b-a)$.
\end{lemma}

\begin{proof}
Take a positively oriented placement and label the vertices $V_1,V_2,V_3$ in counterclockwise
order with interior angles $\alpha,\beta,\gamma$ respectively; let $e_i$ be the directed edge from
$V_i$ to $V_{i+1}$ (indices mod $3$). Then $e_1,e_2,e_3$ are opposite $V_3,V_1,V_2$, so they have
lengths $c,a,b$. Traversing counterclockwise turns left at $V_{i+1}$ by the exterior angle
$\pi-(\text{angle at }V_{i+1})$, so
$\mathrm{dir}(e_2)=\mathrm{dir}(e_1)+(\pi-\beta)$ and
$\mathrm{dir}(e_3)=\mathrm{dir}(e_2)+(\pi-\gamma)$. Now $\pi$ adds $3$ to the $\frac\pi3$-coefficient
$j$, while $\alpha$ adds $0$, $\beta=\frac\pi3-\alpha$ adds $1$, and $\gamma=\frac{2\pi}3$ adds $2$;
so $\pi-\beta$ adds $3-1=2$ and $\pi-\gamma$ adds $3-2=1$. Writing $j_0$ for the
$\frac\pi3$-coefficient of $\mathrm{dir}(e_1)$, the three coefficients are $j_0,\,j_0+2,\,j_0+3$, so
$f_\alpha=(-1)^{j_0}$ on $e_1,e_2$ and $-(-1)^{j_0}$ on $e_3$. As $e_1,e_2,e_3$ carry lengths
$c,a,b$,
\[
C_{f_\alpha}(t)=(-1)^{j_0}\bigl(c+a-b\bigr).
\]
Any placement is obtained from this one by a grid rotation $m\alpha+n\frac\pi3$, which shifts every
$j$ by $n$ and multiplies $C_{f_\alpha}$ by $(-1)^n$, possibly followed by a reflection, which
reverses the traversal and negates $C_{f_\alpha}$; hence $C_{f_\alpha}(t)=\pm(c+a-b)$ in every case.
Repeating in the $\beta$-frame (where $\gamma=\frac{2\pi}3$ adds $0$ to $j'$ and $\alpha$ adds $1$)
makes the $a$-edge the odd one out, giving $C_{f_\beta}(t)=\pm(c+b-a)$.
\end{proof}

\begin{corollary}[Integrality and parity]\label{cor:int}
Each of $M_\alpha=\dfrac{\Phi_{f_\alpha}(\partial ABC)}{c+a-b}$ and
$M_\beta=\dfrac{\Phi_{f_\beta}(\partial ABC)}{c+b-a}$ is an integer, and moreover
\[
M_\alpha\equiv M_\beta\equiv N \pmod 2 .
\]
They are separate necessary conditions: each follows from Lemma~\ref{lem:cancel} for its own $f$,
so a single failure forbids a tiling.
\end{corollary}

\begin{proof}
By Lemmas \ref{lem:cancel} and~\ref{lem:value}, $\Phi_{f_\alpha}(\partial ABC)=\sum_t C_{f_\alpha}(t)
=(c+a-b)\sum_t\varepsilon_t$ with $\varepsilon_t\in\{\pm1\}$, so $M_\alpha=\sum_t\varepsilon_t$
is a sum of $N$ signs, whence $M_\alpha\equiv N\pmod 2$; likewise for $f_\beta$.
\end{proof}

\section{The isosceles obstruction}\label{sec:isosceles}

\begin{lemma}[Non-integrality]\label{lem:nonint}
Let $a,k$ be positive integers with $\gcd(a,k)=1$, put $b=k^2$, and let $c>0$ satisfy
$c^2=a^2+ab+b^2$. Then $k\nmid(a+b-c)$.
\end{lemma}

\begin{proof}
From $c^2=a^2+ab+b^2$ we get $c>a$ and, since $c^2<(a+b)^2$, also $c<a+b$. Suppose
$k\mid(a+b-c)$. As $b=k^2\equiv0\pmod k$, this gives $c\equiv a\pmod k$; with $0<c-a<b=k^2$ we may
write $c=a+kt$, $1\le t\le k-1$. Substituting into $c^2=a^2+ak^2+k^4$ and dividing by $k$,
\[
2at+kt^2=ak+k^3,\qquad\text{that is}\qquad a(2t-k)=k(k-t)(k+t).
\]
Then $k\mid a(2t-k)$, and $\gcd(a,k)=1$ gives $k\mid(2t-k)$, hence $k\mid 2t$. But $2\le2t\le2k-2$
contains no multiple of $k$ other than $k$ itself, so $2t=k$. The left side is then $a(2t-k)=0$,
while the right side is $k\cdot\frac k2\cdot\frac{3k}2=\frac{3k^3}4>0$, a contradiction. Hence
$k\nmid(a+b-c)$.
\end{proof}

\begin{theorem}\label{thm:iso}
Let $T$ be a tile with angles $(\alpha,\beta,2\pi/3)$, $\alpha/\pi$ irrational. Then no prime number
of copies of $T$ tiles an isosceles, non-equilateral triangle.
\end{theorem}

\begin{remark}\label{rem:incomm}
The irrationality hypothesis cannot be dropped: the commensurable tile
$(\frac\pi6,\frac\pi6,\frac{2\pi}3)$ tiles an equilateral (hence isosceles) triangle with $N=3$, by
the fan from the centre; that tile lives in the commensurable branch of the classification, where
$N=3n^2$ is allowed. The equilateral target for an \emph{incommensurable} $2\pi/3$ tile is excluded
for primes by Beeson~\cite{BeesonEq}, and is covered in the assembly of Section~\ref{sec:assembly};
it is not part of this theorem.
\end{remark}

\begin{proof}
$ABC$ has exactly two equal corner angles. Each corner angle is $m\alpha+k\frac\pi3$
(Section~\ref{sub:shapes}); since $\alpha/\pi$ is irrational, two corner angles are equal only if
their pairs $(m,k)$ coincide. So the corner-type triple of $ABC$ has exactly one repeated type, and
among the eleven triples of Section~\ref{sub:shapes} exactly the two isosceles ones qualify. Hence
the base angle is $\alpha$ or $\beta$. We use the invariant generated by the base angle, so that the
equal sides land on $\frac\pi3$-coefficient $3$ (odd) and pick up $f=-1$.

If the base angle is $\alpha$, then $ABC=k(c,c,2b+a)$ (equal sides $kc$, base $k(2b+a)$): the base
is at direction $0$ ($f_\alpha=+1$) and the equal sides at $\pi-\alpha=3\frac\pi3-\alpha$
($f_\alpha=-1$), so $\Phi_{f_\alpha}(\partial ABC)=k(2b+a)-2kc=k(2b+a-2c)$. The tiling count is
$N=k^2(a+2b)/b$; since $N$ is prime and $\gcd(a+2b,b)=1$, we have $k^2=b$, i.e.\ $k=\sqrt b$.
By Corollary~\ref{cor:int} and $c^2=a^2+ab+b^2$,
\[
\frac{k(2b+a-2c)}{c+a-b}=\frac{c-a-b}{k}\in\Z,\qquad k=\sqrt b,
\]
so $k\mid(a+b-c)$, contradicting Lemma~\ref{lem:nonint}. If the base angle is $\beta$, then
$ABC=k(c,c,2a+b)$, the equal sides are at $\pi-\beta$, and using $f_\beta$ (for which the equal
sides have $\frac\pi3$-coefficient $3$) the same computation gives, with $k=\sqrt a$,
$(c-a-b)/k\in\Z$, again contradicting Lemma~\ref{lem:nonint} (the integer $a+b-c$ is symmetric in
$a,b$). In both cases no tiling exists.
\end{proof}

\begin{remark}
The role of the two invariants is essential. For the base-angle-$\beta$ shape, $f_\alpha$ places
the equal sides at $\pi-\beta=\frac{2\pi}3+\alpha$, an \emph{even} $\frac\pi3$-coefficient, so
$f_\alpha$ gives an integer value and does not obstruct; $f_\beta$ does. Each invariant is a
necessary condition in its own right (Corollary~\ref{cor:int}), so using the one that fails is
legitimate, not a choice of convenient frame: on any genuine tiling both invariants return an
integer.
\end{remark}

\section{Resolution of the problem}\label{sec:assembly}

\begin{proof}[Proof of Theorem~\ref{thm:main}]
Let $p>3$ be prime with $p\equiv3\pmod4$, and suppose some triangle is $p$-tiled. By the
classification (Section~\ref{sec:prelim}) the tile is in one of the listed types, and every type
other than a $2\pi/3$ tile on a non-equilateral triangle excludes such a $p$ by an existing theorem
\cite{SWW, BeesonI, BeesonSeven, BeesonIII, BeesonIso, BeesonEq}. For a $2\pi/3$ tile,
Proposition~\ref{prop:reduction} forces $ABC$ isosceles and not equilateral, and
Theorem~\ref{thm:iso} excludes that. Hence no such tiling exists. Finally $19>3$ is prime and $\equiv3\pmod4$, so no triangle is cut into
$19$ congruent triangles.
\end{proof}

\section{Towards the full problem}\label{sec:full}

Erd\H{o}s's question asks for \emph{all} $N$. Theorem~\ref{thm:main} settles the negative side for
primes; this section records what the present methods contribute to the full determination: a
complete answer for primes, and, for each sporadic $2\pi/3$ branch, a determination of its
\emph{admissible spectrum} --- the set of counts compatible with the area and invariant conditions.

\begin{theorem}[The prime case, complete]\label{thm:primefull}
A prime $p$ is a number of congruent triangles into which some triangle can be cut if and only if
$p=2$, $p=3$, or $p\equiv 1\pmod 4$.
\end{theorem}

\begin{proof}
\emph{If.} For $p=2$, the altitude from the right angle splits an isosceles right triangle into two
congruent triangles. For $p=3$, join the centre of an equilateral triangle to its vertices. For
$p\equiv1\pmod4$, Fermat's two-squares theorem gives $p=e^2+f^2$ with $e,f\ge1$; splitting a right
triangle with legs $e,f$ by the altitude from the right angle and tiling the two similar pieces
quadratically with $e^2$ and $f^2$ congruent copies realizes $N=e^2+f^2$ (the biquadratic tiling
\cite{Soifer, BeesonIso}). \emph{Only if.} Theorem~\ref{thm:main}, whose dependencies this
direction inherits.
\end{proof}

\begin{theorem}[Isosceles admissible spectrum]\label{thm:admissible}
Let $(a,b,c)$ be a primitive $120^\circ$-triple and write $b=de^2$ with $d$ squarefree. Every
$N$-tiling of the base-$\alpha$ isosceles target has scale $k=dew$ for a positive integer $w$, and
\[
N=d\,w^2\,(a+2b),\qquad e\mid w\,(c-a-b),\qquad \frac{w(c-a-b)}{e}\equiv N\pmod 2 .
\]
Symmetrically, with $a=d'e'^2$, the base-$\beta$ target forces $N=d'w^2(2a+b)$,
$e'\mid w(c-a-b)$ and the same parity for $w(c-a-b)/e'$.
\end{theorem}

\begin{proof}
By the area identity $Nb=k^2(a+2b)$ and $\gcd(a+2b,b)=1$ we get $b\mid k^2$. For a prime
$p\mid d$ the valuation $v_p(b)=2v_p(e)+1\le 2v_p(k)$ forces $v_p(k)\ge v_p(e)+1$, and for
$p\nmid d$, $v_p(k)\ge v_p(e)$; hence $de\mid k$, say $k=dew$, and substituting back,
$N=dw^2(a+2b)$. By Corollary~\ref{cor:int} and the identity $(c-a-b)(c+a-b)=b(2b+a-2c)$, the
invariant value is $M=k(c-a-b)/b$, so $b\mid k(c-a-b)$, i.e.\ $de^2\mid dew(c-a-b)$, i.e.\
$e\mid w(c-a-b)$; and $M=w(c-a-b)/e\equiv N\pmod2$ by Corollary~\ref{cor:int}.
\end{proof}

\noindent Theorem~\ref{thm:iso} is the degenerate case: $N$ prime forces $d=w=1$, so $b=e^2$ and
$e\mid(c-a-b)$, which Lemma~\ref{lem:nonint} refutes. The residual divisibility is governed by the
following classification.

\begin{proposition}[Solvability of $e\mid(a+b-c)$]\label{prop:solv}
Let $b=de^2$, $d$ squarefree, $\gcd(a,b)=1$. Then $e\mid(a+b-c)$ holds for a primitive
$120^\circ$-triple if and only if there is an integer $j$ with $d<j<2d$ such that $ej$ is even,
\[
a=\frac{e^2(2d-j)(2d+j)}{4(j-d)}
\]
is a positive integer coprime to $de^2$; in that case $c=a+\tfrac{e^2 j}{2}$. In particular, for
$d=1$ the range $(1,2)$ contains no integer, which re-proves Lemma~\ref{lem:nonint}; for $d=2$,
$j=3$, $e=2$ one obtains $(a,b,c)=(7,8,13)$.
\end{proposition}

\begin{proof}
Since $e\mid b$, the hypothesis gives $c\equiv a\pmod e$, and $0<c-a<b$ writes $c=a+et$ with
$1\le t\le de-1$. Substituting into $c^2=a^2+ab+b^2$ and dividing by $e$,
$a(2t-de)=e(de-t)(de+t)$. As $e\mid a(2t-de)$ and $\gcd(a,e)=1$, we get $e\mid 2t$, say $2t=ej$
with $1\le j\le 2d-1$; substituting $t=ej/2$ gives $4a(j-d)=e^2(2d-j)(2d+j)$, whose right side is
positive, forcing $j>d$ and the displayed formula. Conversely, given such $j$, setting
$t=ej/2$, $a$ as displayed and $c=a+et$ reverses the computation: $c^2=a^2+ab+b^2$ and
$a+b-c=e(de-t)$ is divisible by $e$.
\end{proof}

\begin{theorem}[Spectrum lattice]\label{thm:lattice}
Let $(a,b,c)$ be a primitive $120^\circ$-triple, $b=de^2$ with $d$ squarefree, $r=c-a-b$,
$g=\gcd(e,r)$, $e_1=e/g$, and
\[
T \;=\; \frac rg + d\,e_1^2\,(a+2b) \pmod 2 .
\]
Set $E=e_1$ if $T$ is even and $E=2e_1$ if $T$ is odd. Then the counts admissible for the
base-$\alpha$ isosceles target (Theorem~\ref{thm:admissible} with the parity clause) are exactly
\[
N=d\,(Eu)^2\,(a+2b),\qquad u=1,2,3,\dots
\]
\end{theorem}

\begin{proof}
By Theorem~\ref{thm:admissible} the conditions on $w$ are $e\mid wr$ and
$wr/e\equiv N\pmod2$. As $\gcd(e_1,r/g)=1$, the divisibility is equivalent to $e_1\mid w$; writing $w=e_1u$, the
count is $M=ur/g$, and using $u^2\equiv u\pmod 2$,
\[
M-N=\frac{ur}{g}-d\,e_1^2u^2(a+2b)\equiv u\Bigl(\frac rg+d\,e_1^2(a+2b)\Bigr)=uT\pmod2,
\]
so the parity clause holds for all $u$ when $T$ is even, and exactly for even $u$ when $T$ is odd.
\end{proof}

Theorem~\ref{thm:lattice} uses only the base-aligned invariant. The mirror invariant is also a
necessary condition on the same target, and it closes the spectrum completely.

\begin{theorem}[Spectrum theorem]\label{thm:spectrum}
Let $(a,b,c)$ be a primitive $120^\circ$-triple. The tile counts satisfying \emph{all} the
invariant conditions on the base-$\alpha$ isosceles target --- integrality and parity of both
$M_\alpha$ and $M_\beta$, together with the area equation --- are exactly Zhang's family
\[
N \;=\; m^2\, b\,(a+2b),\qquad m=1,2,3,\dots
\]
Symmetrically, the base-$\beta$ target admits exactly $N=m^2a(2a+b)$, and the $F_1$ target
exactly $N=m^2b(a+b)$.
\end{theorem}

\begin{proof}
Write $X=c+a-b$, $Y=c+b-a$, so $XY=3ab$ by~\eqref{eq:tile}. On the base-$\alpha$ target with
scale $k$, $M_\alpha=k(2b+a-2c)/X$ and $M_\beta=k(2b+a+2c)/Y$ (the equal sides carry
$\frac\pi3$-coefficient $3$ in the $\alpha$-frame and $2$ in the $\beta$-frame). Since
$(2b+a-2c)+2X=3a$ and $(2b+a+2c)-2Y=3a$, the two integralities are equivalent to
\[
X\mid 3ak \qquad\text{and}\qquad Y\mid 3ak,
\]
and, setting $A=3ak/X$, $B=3ak/Y$, the parity clauses of Corollary~\ref{cor:int} read
$A\equiv B\equiv N\pmod 2$. Recall $k=dew$ and $N=dw^2(a+2b)$, with $b=de^2$.

If $e\mid w$, say $w=em$, then $k=de^2m=bm$, so $A=Ym$ and $B=Xm$ are integers, and
$A-N\equiv m\bigl(Y+b(a+2b)\bigr)\pmod 2$ using $m^2\equiv m$; now
$Y+b(a+2b)\equiv c+a+b+ab\equiv 0\pmod2$, because~\eqref{eq:tile} gives $c\equiv a+b+ab$;
likewise for $B$. So every member of Zhang's family is admissible.

Conversely, fix a prime $p$ and let $x,y,\sigma,\varepsilon,\delta,\omega$ be the $p$-adic
valuations of $X,Y,3a,e,d,w$; then $x+y=\sigma+\delta+2\varepsilon$ and the divisibilities give
$\max(x,y)\le\sigma+\delta+\varepsilon+\omega$, so
$\omega\ge\varepsilon-\min(x,y)$. A common prime of $X$ and $Y$ divides $X+Y=2c$ and
$Y-X=2(b-a)$; for odd $p$ this forces $p\mid c$ and $p\mid b-a$, whence $3\mid c$ or
$p\mid\gcd(a,b)$ --- both impossible ($3\nmid c$ as in Proposition~\ref{prop:reduction}). So
$\min(x,y)=0$ for every odd $p$, and $\omega\ge\varepsilon$ there. At $p=2$: if $ab$ is odd
then $X,Y$ are odd and the same argument applies. If $b$ is even (so $a$ is odd), a two-line
computation modulo $8$ shows $v_2(b)\notin\{1,2\}$: $b\equiv2\pmod4$ gives
$c^2\equiv1+2\equiv3\pmod4$, and $v_2(b)=2$ gives $c^2\equiv1+4\equiv5\pmod8$, both
impossible. So $v_2(b)\ge3$. Here $v_2(X+Y)=v_2(2c)=1$ forces $\min(x,y)=1$, and the
divisibilities alone allow $\omega=\varepsilon-1$; but then exactly one of $A,B$ is odd
(their $2$-valuations are $0$ and $v_2(b)-2$), while
$v_2(N)=\delta_2+2\omega=v_2(b)-2\ge1$ makes $N$ even --- so the parity clause fails, and
$\omega\ge\varepsilon$ at $p=2$ as well. Hence $e\mid w$, i.e.\ $N=m^2b(a+2b)$.
The base-$\beta$ case is the mirror $a\leftrightarrow b$. For $F_1$ the counts are
$M_\alpha=3ak/X-k$ and $M_\beta=3ak/Y+k$ (Section~\ref{sub:frontier}), so the same
divisibilities appear, the parity clauses read $A\equiv B\equiv N+k\pmod2$, and in the
boundary case $v_2(k)=\delta_2+2\varepsilon_2-1\ge2$ makes $N+k$ even against an odd count;
the argument is otherwise identical, giving $N=m^2b(a+b)$.
\end{proof}

\begin{remark}\label{rem:zhang}
The single-invariant lattice of Theorem~\ref{thm:lattice} can be strictly coarser than $e\Z$
(the smallest example is $(11,24,31)$, whose lattice admits $N=354$), which briefly suggested
admissible values beyond Zhang's constructions. Theorem~\ref{thm:spectrum} corrects this: the
mirror invariant eliminates every such value ($354$ by parity, $15689$ on $(19,261,271)$ already
by integrality), and the fully refined spectrum \emph{coincides with Zhang's family on every
tile} --- verified exhaustively over all $138$ primitive triples with $a,b<400$. The necessary
side of the isosceles and $F_1$ branches is therefore closed. What remains open in these branches
is exactly the realizability of the \emph{small} family members. Not all of them are open:
a family member that is also a sum of two squares (or $2$, $3$, $6$ times a square) is realized by
the commensurable construction~\cite{BeesonSeven}, so the genuinely undecided members are precisely
those with a prime $\equiv3\pmod4$ to an odd power. (Thus $N=40=b(a+b)$ on $(3,5,7)$ is realized
as $2^2+6^2$, and $N=65=b(a+2b)$ on $(3,5,7)$ as $1^2+8^2$, while $105=3\cdot5\cdot7$ is not a sum
of two squares.) Zhang's constructions cover $m$ in certain residue classes from some bound onward,
so the sharpest open instances are the smallest such members: $N=105=b(a+b)=7\cdot15$ on the
$F_1$ target $(105,56,91)$ of the tile $(8,7,13)$, then $120$, $132$, $154$, $184$. Each has
membership undecided by any known necessary condition, and is exactly the kind of bounded
existence question the engine of Section~\ref{sub:frontier} addresses --- though for $N$ of this
size a complete exhaustive search is not yet computationally in reach.
\end{remark}

\begin{remark}\label{rem:necessary}
Admissibility is necessary, not sufficient. The smallest admissible value is $N=33=3\cdot 11$ on
the tile $(5,3,7)$ (where $d=3$, $e=1$, so the divisibility is vacuous); it is nevertheless
excluded by Beeson's boundary analysis, which rules out $N<36$~\cite{BeesonIso}, while Herdt's
$2673$-tile tiling is the member $w=9$ of the same family $33w^2$. The parity clause bites hard: on the tile $(7,8,13)$ (where $d=2$, $e=2$, $c-a-b=-2$) the
divisibility admits all $N=2w^2\cdot23$, but the count $M=-w$ must have the parity of
$N=2w^2\cdot 23$, which is even --- forcing $w$ even, say $w=2m$; the refined spectrum is exactly
$N=184m^2=m^2\,b(a+2b)$ --- \emph{precisely} Zhang's
constructed family~\cite{Zhang} for this tile. In particular $N=46$, previously the smallest value
passing every known necessary condition on this branch, is \emph{excluded} (Section~\ref{sub:frontier}
checks the remaining branches), in exact agreement with the prediction of Zhang's conjecture.
Zhang's constructions realize $N=m^2b(a+2b)$ for $m$ in certain residue classes; the refined
spectrum bounds the realized set from outside, and Theorem~\ref{thm:lattice} determines it
exactly.
\end{remark}

\begin{proposition}[The other branches]\label{prop:otherspectra}
With the same normalizations:
$F_1$ forces $N=dw^2(a+b)$ where $b=de^2$, $d$ squarefree (from $b\mid k^2$ as above);
$F_2,F_3,F_4$ force $N=N_0k^2$ exactly, with $N_0=(a+2b)(2a+b)$, $3(a+b)(a+2b)$, $(a+b)(2a+b)$;
the tile-similar shape forces $N=n^2$; and an equilateral target of side $S$ forces $ab\mid S^2$,
$N=S^2/(ab)$ (so $N$ and $ab$ have the same squarefree kernel) together with
$(c+a-b)\mid 3S$ and $(c+b-a)\mid 3S$.
\end{proposition}

\begin{proof}
The scalene statements are the area identity~\eqref{eq:area} with the side-vectors of
Section~\ref{sec:reduction} ($F_1$ repeats the $b\mid k^2$ analysis). For the equilateral target
the three sides, traversed counterclockwise, differ in direction by $\frac{2\pi}3=2\cdot\frac\pi3$,
so $f$ takes one sign on all three and $\Phi_f(\partial ABC)=\pm3S$ for both invariants;
Corollary~\ref{cor:int} gives the two divisibilities, and the area identity gives $N\,ab=S^2$.
\end{proof}

\subsection*{The equilateral $2\pi/3$ spectrum.}
The equilateral divisibilities of Proposition~\ref{prop:otherspectra} reduce to a clean finite
criterion.

\begin{proposition}[Equilateral admissibility]\label{prop:eqspec}
Let an equilateral triangle of side $S$ be $N$-tiled by a $2\pi/3$ tile $(a,b,c)$, and put
$X=c+a-b$, $Y=c+b-a$. Then $XY=3ab$, and $s:=3S/X$, $t:=3S/Y$ are positive integers with
\[
st=3N,\qquad s\equiv t\equiv N\pmod 2,\qquad (t-s)^2+16N=q^2\ \text{ for an integer } q;
\]
conversely $(s,t,q)$ determine the instance:
$(a,b,c)$ is proportional to $\bigl(q+(t-s),\,q-(t-s),\,2(s+t)\bigr)$, and primitivity pins the
scale, hence $S$.
\end{proposition}

\begin{proof}
$XY=c^2-(a-b)^2=3ab$ by~\eqref{eq:tile}. By Proposition~\ref{prop:otherspectra}, $X\mid 3S$ and
$Y\mid 3S$, so $s,t\in\Z_{\ge1}$; indeed $s=M_\alpha$ and $t=M_\beta$ are the two invariant
counts, so $s\equiv t\equiv N\pmod2$ by Corollary~\ref{cor:int}, and
$st=9S^2/(XY)=9\,Nab/(3ab)=3N$. From $X-Y=2(a-b)$ we get
$a-b=\tfrac{3S}{2}\bigl(\tfrac1s-\tfrac1t\bigr)=\tfrac{S(t-s)}{2N}$, and $4ab=4S^2/N$ gives
$(a+b)^2=(a-b)^2+4ab=\tfrac{S^2}{4N^2}\bigl[(t-s)^2+16N\bigr]$; as $a+b$ is an integer,
$q:=2N(a+b)/S$ is a rational with integer square, hence an integer, and
$(t-s)^2+16N=q^2$. Then $a-b$, $a+b$ and $c=(X+Y)/2=\tfrac{S(s+t)}{2N}$ give the displayed
proportions.
\end{proof}

\subsection*{The equilateral criteria as divisor conditions.}
Both equilateral square criteria --- ours and Beeson's --- complete the square.

\begin{proposition}[Conic form]\label{prop:conic}
For an equilateral target: a $2\pi/3$ tile requires a factorization $uv=16N^2$ with
$u+v\equiv0\pmod2$ and $\tfrac{u+v}2-5N=s^2$ for a divisor $s$ of $3N$ with
$s\equiv 3N/s\equiv N\pmod2$; a $\pi/3$ tile requires a factorization $uv=16N^2$ with
$\tfrac{u+v}2 = 5N-M^2$ for some $0<M<\sqrt N$, $M\equiv N\pmod 2$. These are equivalent to
the criteria of Proposition~\ref{prop:eqspec} and of~\cite[Thm.~3]{BeesonEq} respectively.
\end{proposition}

\begin{proof}
For the $2\pi/3$ case, with $t=3N/s$ the condition $(t-s)^2+16N=q^2$ becomes, after multiplying
by $s^2$, $(qs)^2=(3N-s^2)^2+16Ns^2=(s^2+N)(s^2+9N)$, i.e.\
$(s^2+5N)^2-(qs)^2=16N^2$; factor the difference of squares. For the $\pi/3$ case,
$(9N-M^2)(N-M^2)=y^2$ is $(5N-M^2)^2-16N^2=y^2$, i.e.\ $(5N-M^2-y)(5N-M^2+y)=16N^2$.
\end{proof}

\noindent The necessary side of the equilateral branch is thus elementary --- a divisor
condition on $16N^2$ --- and, per $N$, pins finitely many fully determined instances. The
elliptic curves of Laczkovich~\cite{LaczkovichEll} concern the \emph{realizability} of such
instances, not their enumeration.

\subsection*{The values $14$ and $15$.}\label{sub:frontier}
The machinery above, combined with the published branch theorems, decides every branch of the
classification for $N=14$ and $N=15$ by finite computations
(\texttt{verify\_frontier.py}): the commensurable, tile-similar, right-angle and
$\gamma=2\alpha$ branches exclude both values by their known $N$-forms; the sporadic
$2\pi/3$ shapes exclude both by the admissible spectra of
Theorems~\ref{thm:admissible} and Proposition~\ref{prop:otherspectra}; the $\pi/3$-tile equilateral
case excludes both by Beeson's square criterion ($(9N-M^2)(N-M^2)$ is a perfect square for some
$M<\sqrt N$~\cite[Thm.~3]{BeesonEq}, which fails for every admissible $M$); and of the five target
shapes of the $3\alpha+2\beta=\pi$ branch~\cite{BeesonIII}, four exclude both values through their
published tiling equations (checked by exact rational-root enumeration), while the isosceles target
with base angles $\alpha+\beta$ admits, for $N=14$, the single candidate tile $(45,56,81)$ with
$M=2$ --- which is destroyed by Beeson's boundary congruence $M\equiv-m\pmod{\gcd(a,c)}$ (it forces
at least seven $b$-edges of length $56$ on a base of length $140$).

What survives everything is four fully explicit finite instances:
\begin{center}
\begin{tabular}{llll}
$N$ & branch & tile & target\\
\hline
$14$ & equilateral, $2\pi/3$ & $(7,8,13)$ & equilateral, $S=28$\\
$15$ & equilateral, $2\pi/3$ & $(3,5,7)$ & equilateral, $S=15$\\
$15$ & $3\alpha+2\beta=\pi$, iso-$(\alpha{+}\beta)$, $M=1$ & $(56,15,64)$ & $(120,120,105)$\\
$15$ & $3\alpha+2\beta=\pi$, iso-$(\alpha{+}\beta)$, $M=3$ & $(4,15,16)$ & $(60,60,15)$\\
\end{tabular}
\end{center}
In each, the tile is \emph{uniquely determined} (Proposition~\ref{prop:eqspec} for the equilateral
rows; the tiling equation $N/M^2=(1+s)/(1-s)$ of~\cite[Thm.~17]{BeesonIII} for the isosceles rows),
so each is a single bounded existence question: can $14$ (resp.\ $15$) congruent copies of the
stated tile fill the stated triangle?

Each instance was settled by an exhaustive, exact search (\texttt{code/engine/}). The engine is an
advancing-front algorithm over $\Q(\sqrt D)$ ($D=3,23,7$; every geometric decision exact, no
floating point) whose branching rule is provably complete: at the lexicographically least vertex
$v$ of the unfilled region --- necessarily convex --- every tile of any tiling whose closure
contains $v$ has a corner there (an edge through $v$ would subtend angle $\pi$), so the
clockwise-most of them has a corner at $v$ with one side along the clockwise boundary ray; this
leaves at most six placements (three corner types, two adjacent sides each, the two choices being
mirror images). An exhausted search is therefore a proof of non-existence. Two prunes are used,
each a theorem about completable states: the area of every region component is a positive integer
multiple of the tile area; and a maximal straight boundary run with \emph{convex} endpoints has
length in $\N a+\N b+\N c$ (whole tile edges cannot pass a convex corner --- runs with a reflex
endpoint are not pruned, as an edge may continue past a reflex corner into the region). The engine
passes positive controls --- it finds the $N=4$ reptile subdivisions in both tile families and a
hand-built non-edge-to-edge two-tile configuration with T-junctions, each found tiling re-verified
by an independent checker --- and, as a robustness check, all four verdicts below are unchanged
when the run prune is disabled entirely (node counts without it in parentheses).
\begin{center}
\begin{tabular}{lllll}
instance & tile & target & verdict & nodes\\
\hline
$N=14$, equilateral & $(7,8,13)$ & $S=28$ & exhausted, no tiling & $133$ \ ($482$)\\
$N=15$, equilateral & $(3,5,7)$ & $S=15$ & exhausted, no tiling & $156$ \ ($604$)\\
$N=15$, iso-$(\alpha{+}\beta)$ & $(56,15,64)$ & $(120,120,105)$ & exhausted, no tiling & $37$ \ ($526$)\\
$N=15$, iso-$(\alpha{+}\beta)$ & $(4,15,16)$ & $(60,60,15)$ & exhausted, no tiling & $2$ \ ($10$)\\
\end{tabular}
\end{center}

\begin{theorem}\label{thm:frontier}
No triangle can be cut into $14$ congruent triangles, and none into $15$.
\end{theorem}

\begin{proof}
By the branch sweep above, any $14$- or $15$-tiling would live in one of the four listed instances,
each with its tile and target uniquely determined; the exhaustive searches refute all four. The
dependencies are those of Theorem~\ref{thm:main} together with \cite[Thms.~3, 7, 11, 14, 17,
19]{BeesonIII}, \cite[Thm.~3]{BeesonEq}, and the declared computer assistance (exact arithmetic,
complete branching, independently validated).
\end{proof}

\subsection*{The values $21$, $22$, $30$, and the instance $46$.}
The same sweep, sharpened by the parity clause of Corollary~\ref{cor:int}, extends further
(\texttt{verify\_frontier.py}). Three remarks carry the new weight. First, the invariant
applies to the \emph{scalene} $F_1$ target: its sides $k(a{+}b),ka,kc$ have
$\frac\pi3$-coefficients $0,2,3$ (the same turning computation as Lemma~\ref{lem:value}), so
\[
M_\alpha=\frac{k(2a+b-c)}{c+a-b},\qquad M_\beta=\frac{k(2a+b+c)}{c+b-a}
\]
must be integers of the parity of $N$. For $N=21$ this destroys the unique structural candidate,
the genuine tile $(5,16,19)$ with $k=4$: $M_\alpha=28/8\notin\Z$ --- while Zhang's constructed
$F_1$ family $N=m^2b(a+b)$ passes, so the invariant separates the candidate from the constructions.
(For $N=30$ the candidate $(7,8,13)$, $k=4$ has $M_\alpha=3$, killed by parity.) Second, for
$N=22$ and $N=30$ \emph{every} branch dies arithmetically --- the two isosceles-$(\alpha{+}\beta)$
candidates of $22$ fall to the boundary congruence, those of $30$ likewise --- so no search is
needed at all. Third, for $N=21$ exactly two instances survive, both isosceles-$(\alpha{+}\beta)$:
$M=1$, tile $(110,21,121)$ on $(231,231,210)$, and $M=3$, tile $(10,21,25)$ on $(105,105,42)$;
both live in $\Q(\sqrt6)$, and the engine exhausts both:
\begin{center}
\begin{tabular}{lllll}
instance & tile & target & verdict & nodes\\
\hline
$N{=}21$, iso-$(\alpha{+}\beta)$, $M{=}1$ & $(110,21,121)$ & $(231,231,210)$ & exhausted & $107$ ($4266$)\\
$N{=}21$, iso-$(\alpha{+}\beta)$, $M{=}3$ & $(10,21,25)$ & $(105,105,42)$ & exhausted & $15$ ($102$)\\
\end{tabular}
\end{center}
Finally, the parity clause settles the value that Remark~\ref{rem:necessary} identified as the
sharpest test of Zhang's conjecture: $N=46$ passes the divisibility spectrum on $(7,8,13)$ but not
the parity, and the sweep excludes every other branch, so $46$ is not realizable --- exactly as
Zhang's conjecture predicts.

The pipeline is now mechanical, and it continues: $N=38$ and $N=42$ die in every branch by
arithmetic alone (both squarefree, so the $\gamma=2\alpha$ branch is closed by
\cite[Thm.~11.7]{BeesonIso}, and no sporadic, equilateral or $3\alpha+2\beta$ candidate survives),
while $33$, $35$ and $39$ each reduce to two isosceles-$(\alpha{+}\beta)$ instances (the
sporadic-$2\pi/3$ candidate $(5,3,7)$ at $N=33$ is excluded by Beeson's $N<36$ boundary
analysis~\cite{BeesonIso}); all six searches exhaust:
\begin{center}
\begin{tabular}{llll}
instance & tile & target & nodes\\
\hline
$N{=}33$, $M{=}1$ & $(272,33,289)$ & $(561,561,528)$ & $489$\\
$N{=}33$, $M{=}3$ & $(28,33,49)$ & $(231,231,132)$ & $49$\\
$N{=}35$, $M{=}1$ & $(306,35,324)$ & $(630,630,595)$ & $523$\\
$N{=}35$, $M{=}5$ & $(6,35,36)$ & $(210,210,35)$ & $2$\\
$N{=}39$, $M{=}1$ & $(380,39,400)$ & $(780,780,741)$ & $853$\\
$N{=}39$, $M{=}3$ & $(40,39,64)$ & $(312,312,195)$ & $67$\\
\end{tabular}
\end{center}

\begin{theorem}\label{thm:frontier2}
No triangle can be cut into $21$, $22$, $30$, $33$, $35$, $38$, $39$, $42$, or $46$ congruent
triangles.
\end{theorem}

\begin{proof}
The sweeps above; for $21$, $33$, $35$ and $39$, additionally the exhaustive searches listed.
Dependencies as in Theorem~\ref{thm:frontier}.
\end{proof}

\subsection*{Decidability.}
The pattern of the last two subsections is not an accident. Every branch of the classification now
reduces, for each fixed $N$, to a \emph{finite} list of fully determined instances: the
commensurable, similar-tile, right-angle and $\gamma=2\alpha$ branches are decided by closed
$N$-forms; in the sporadic $2\pi/3$ shapes the divisor structure of $N$ (Theorems
\ref{thm:admissible}, \ref{thm:lattice}, Proposition~\ref{prop:otherspectra}) leaves finitely
many (tile, scale) pairs; the equilateral cases pin the tile from finitely many factorizations
(Proposition~\ref{prop:eqspec}) or coloring numbers (\cite[Thm.~2]{BeesonEq}, which determines
the tile from $(N,M)$); and the five $3\alpha+2\beta=\pi$ shapes have finitely many $(M,s)$
candidates by their tiling equations~\cite{BeesonIII}. Each surviving instance is a bounded
existence question, and the corner-anchored search of \texttt{code/engine/} decides it in
finitely many steps (the branching is provably complete and the depth is $N$). Hence:

\begin{theorem}[Decidability]\label{thm:decidable}
It is decidable, given $N$, whether some triangle can be cut into $N$ congruent triangles
(under the same cited inputs as Theorem~\ref{thm:main}).
\end{theorem}

\noindent This extends the decidability that Beeson established for equilateral
targets~\cite[Thm.~4]{BeesonEq} to the whole problem. What decidability does \emph{not} give is
a closed-form description of the set. After Theorem~\ref{thm:spectrum} and
Proposition~\ref{prop:conic}, the necessary side is closed in \emph{every} branch --- the
admissible values are Zhang's families in the sporadic shapes and explicit divisor-instances in
the equilateral cases --- so the entire residual openness of the problem is a single question:
\emph{which admissible instances are realized}. Zhang's trapezoid constructions realize the
sporadic families for $m\ge9$ in residue classes, and Laczkovich's elliptic-curve
analysis~\cite{LaczkovichEll} governs equilateral realizability; the open kernel is the small
members that are not already realized commensurably --- sharpest $N=105$ on the $F_1$ target of
$(8,7,13)$ --- and each such instance is individually decidable (Theorem~\ref{thm:decidable}).

\begin{remark}[no invariant decides realizability]\label{rem:conserved}
The directional invariants are \emph{conserved} by the tiling process: each tile carries value
$\pm(c+a-b)$ for $f_\alpha$ (resp.\ $\pm(c+b-a)$ for $f_\beta$), so placing one tile changes
$\Phi_f$ of the unfilled region by $\pm V$ and the number of remaining tiles by one --- in step,
so that $\Phi_f/V$ stays integral and keeps the parity of the tile count throughout. Hence the
only conditions such an invariant imposes are the admissibility conditions of
Theorem~\ref{thm:spectrum}, and \emph{no} additive boundary invariant can distinguish an admissible
target from a partially tiled one; none can obstruct an admissible instance, and none prunes the
search below its combinatorial size. For the sharpest open instance $N=105$ we confirmed this
computationally: searching all directional weights of period $\le4$ in the $\alpha$-winding
(reflections included), the only invariants are $f_\alpha$ ($M_\alpha=5$) and $f_\beta$
($M_\beta=21$), both admissible; and the vertex-type balance forced by the angle relations
$a\alpha+b\beta+c\gamma\in\{\pi,2\pi\}$ admits $42{,}282$ nonnegative integer solutions. Deciding
realizability of an admissible instance therefore lies beyond every linear or coloring invariant;
it is a genuinely combinatorial question, which is why the search of Theorem~\ref{thm:decidable}
appears to be essential and why Zhang's conjecture is hard at its sharpest point.
\end{remark}

\subsection*{State of the full problem.}
Assembling: the commensurable branch is completely determined (squares, sums of two squares, and
$2,3,6$ times squares, all realized \cite{BeesonSeven}); the similar-tile and right-angle branches
are settled in \cite{BeesonI, SWW}; the primes are settled by Theorem~\ref{thm:primefull}. What
remains open for the full determination of the tile-count set is: sufficiency in the sporadic
$2\pi/3$ branches (Zhang's completeness conjecture~\cite{Zhang}; the admissible spectra above are
the outer bounds), the $3\alpha+2\beta=\pi$ and $\gamma=2\alpha$ branches beyond the partial
results of \cite{BeesonIII, BeesonIso}, and the equilateral targets for incommensurable tiles,
where Laczkovich has connected the possible $N$ to rational points on elliptic
curves~\cite{LaczkovichEll}. With $7$ and $11$ excluded by \cite{BeesonSeven}, the primes by Theorem~\ref{thm:primefull},
and $14,15,21,22,30,33,35,38,39,42,46$ by Theorems \ref{thm:frontier} and~\ref{thm:frontier2}, the
membership of every $N\le 43$ is now determined ($42$ dies in every branch by the same squarefree
and arithmetic sweep that excludes $22$, $30$, $38$; $43$ is a prime $\equiv3\pmod4$); the smallest
undetermined value, to our knowledge, is $N=44$.

\subsection*{Standing of the inputs.}
For the record, the external inputs to Theorem~\ref{thm:main} and their publication status:
Laczkovich's classification papers \cite{Laczkovich1995,Laczkovich2012} and the rep-tiling theorem
of Snover--Waiveris--Williams \cite{SWW} are refereed journal articles, and Beeson's isosceles
paper \cite{BeesonIso} is accepted (to appear in \emph{Integers}); Beeson's remaining branch papers
\cite{BeesonI,BeesonIII,BeesonSeven,BeesonEq} and the Beeson--Zhang rationality
theorem~\cite{BeesonZhang}, which is load-bearing for the integrality of the tile, are arXiv
preprints at the time of writing. Zhang's constructions~\cite{Zhang} are cited for context only and
carry no logical weight here. The parts original to this paper (Sections
\ref{sec:reduction}--\ref{sec:isosceles} and \ref{sec:full}, together with the shape enumeration
of Section~\ref{sub:shapes}) are self-contained given those inputs, with the arithmetic layer
machine-checked (Section~\ref{sec:verification}).

\section{Verification}\label{sec:verification}

The finite and numerical claims are checked by the scripts in the repository (exact arithmetic).
\texttt{verify\_shapes.py} reproduces the eleven-shape enumeration of Section~\ref{sub:shapes} and
the values $N_0$ of Section~\ref{sec:reduction}. \texttt{verify\_invariant.py} confirms
Lemma~\ref{lem:value} ($C_f(t)=\pm(c+a-b)$ over all orientations of $T$), Lemma~\ref{lem:cancel}
(both sides agree on explicit subdivision tilings, and~\eqref{eq:antisym} cancels at a
non-edge-to-edge incidence), and Lemma~\ref{lem:nonint} (no counterexample among primitive
$120^\circ$-triples up to $c\approx 9\times10^6$). \texttt{verify\_spectrum.py} checks
Section~\ref{sec:full}: the two-positive-squares decomposition for all primes
$p\not\equiv3\pmod4$ below $10^5$; the scale structure $b\mid k^2\iff de\mid k$; the admissible
spectrum of Theorem~\ref{thm:admissible} (no prime is admissible; $33$ and $46$ are); and that
every instance of $e\mid(a+b-c)$ with $a,b<3000$ arises from the $j$-classification of
Proposition~\ref{prop:solv}, with none for $d=1$. As a positive control, both necessary conditions
of Theorem~\ref{thm:iso} hold on the genuine $2673$-tile isosceles tiling of
Herdt~\cite{BeesonIso}: for its tile $(5,3,7)$ and scale $k=27$, $N=k^2(a+2b)/b=2673$ and
$M=k(2b+a-2c)/(c+a-b)=-9$ are integers, as they must be on any true tiling.

The entire \emph{arithmetic and combinatorial} layer of the proof is formalized and machine-checked
in Lean~4 with Mathlib (\texttt{lean/Erdos634.lean}, twenty-three theorems); every theorem depends only
on the standard axioms \texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}, with no
\texttt{sorry}:
\begin{itemize}
\item[] \texttt{shape\_enumeration}: the eleven-triple completeness of Section~\ref{sub:shapes} ---
realizable corner types with $\sum m_i=0$, $\sum k_i=3$ are exactly the eleven listed --- as pure
integer arithmetic;
\item[] \texttt{k\_not\_dvd\_sum\_sub}, \texttt{M\_not\_int}: Lemma~\ref{lem:nonint}
($(c-a-b)/\sqrt b\notin\Z$);
\item[] the full arithmetic of Theorem~\ref{thm:iso} in one master statement: no prime $N$
satisfies the $120^\circ$-relation, the area equation $Nb=k^2(a+2b)$, and the integrality
$(c+a-b)\mid k(2b+a-2c)$ simultaneously (\texttt{iso\_reduction\_identity},
\texttt{prime\_count\_forces\_scale}, \texttt{no\_prime\_isosceles\_count});
\item[] \texttt{add\_not\_prime}, \texttt{not\_prime\_of\_two\_le},
\texttt{F1\_count\_not\_prime}--\texttt{F4\_count\_not\_prime}: the scalene counts of
Proposition~\ref{prop:reduction} are composite ($a+b$ is never prime for a primitive
$120^\circ$-triple, and the $F_2,F_3,F_4$ counts factor);
\item[] \texttt{prime\_three\_mod\_four\_excluded}: a prime $p\equiv3\pmod4$ with $p>3$ is
neither a square, a sum of two squares, nor $2n^2$, $3n^2$ or $6n^2$ (the commensurable branch of
Section~\ref{sec:prelim}), via Fermat's two-squares theorem;
\item[] \texttt{prime\_sum\_two\_pos\_squares}: a prime $p\not\equiv3\pmod4$ is a sum of two
\emph{positive} squares (the achievability half of Theorem~\ref{thm:primefull});
\item[] \texttt{iso\_admissible}: Theorem~\ref{thm:admissible} --- given $b=de^2$ with $d$
squarefree, the area equation and $\Phi$-divisibility force $k=dew$, $N=dw^2(a+2b)$ and
$e\mid w(c-a-b)$;
\item[] the finite arithmetic of the frontier sweeps, in eight theorems: the
$\pi/3$-equilateral square criterion fails at $14$ and $15$; the first tiling equation has no
admissible solution there; the two equilateral factor-pair uniqueness statements; the boundary
congruences that kill the isosceles candidates at $14$ and $22$; the $F_1$ invariant kill at
$21$; and the parity kill of $46$.
\end{itemize}
What is \emph{not} formalized is exactly the geometry: the direction grid of
Section~\ref{sec:prelim} and Lemmas~\ref{lem:cancel} and~\ref{lem:value}, which are proved in the
text and checked numerically; Mathlib has no theory of planar dissections.

\section*{Acknowledgements}

This work was carried out with substantial assistance from an artificial-intelligence system
(Anthropic's Claude), which proposed the signed-direction invariant, performed the symbolic and
numerical verification, found the elementary proof of Lemma~\ref{lem:nonint}, and produced the Lean
formalization, under the author's direction and review. The argument depends on the cited
classification of Laczkovich and Beeson for the branches other than the $2\pi/3$ tile, and on the
rationality theorem of Beeson and Zhang; the shape list coincides with Zhang's six sporadic
types~\cite{Zhang}. The present contribution is the invariant of Section~\ref{sec:invariant}, the
consequent exclusion of \emph{every} prime for the isosceles $2\pi/3$ branch (where Beeson had ruled
out only $N<36$ and left primality open), and the self-contained reduction of the scalene types. Its
arithmetic layer is machine-checked (Section~\ref{sec:verification}); the two geometric lemmas rest
on written proofs supported by numerical checks, and the whole is offered for independent
refereeing.

\begin{thebibliography}{99}

\bibitem{BeesonI} M.~Beeson, \emph{Triangle tiling I: The tile is similar to ABC or has a right
angle}, arXiv:1206.2231.

\bibitem{BeesonIII} M.~Beeson, \emph{Triangle tiling III: the case $3\alpha+2\beta=\pi$},
arXiv:1206.2229.

\bibitem{BeesonIso} M.~Beeson, \emph{Tilings of an isosceles triangle}, arXiv:1206.1974; to appear
in Integers.

\bibitem{BeesonSeven} M.~Beeson, \emph{No triangle can be cut into seven congruent triangles},
arXiv:1811.09723.

\bibitem{BeesonEq} M.~Beeson, \emph{Tiling an equilateral triangle}, arXiv:1812.07014.

\bibitem{BeesonZhang} M.~Beeson and Y.~X.~Zhang, \emph{Rationality of certain triangle tilings},
arXiv:2604.01314.

\bibitem{Zhang} Y.~X.~Zhang, \emph{Tiling triangles with $2\pi/3$ angles}, arXiv:2512.22696.

\bibitem{Erdos633} M.~Beeson, M.~Laczkovich and Y.~X.~Zhang, \emph{Solution of Erd\H{o}s
Problem~633}, arXiv:2604.03609.

\bibitem{Laczkovich1995} M.~Laczkovich, \emph{Tilings of triangles}, Discrete Math.\ \textbf{140}
(1995), 79--94.

\bibitem{Laczkovich2012} M.~Laczkovich, \emph{Tilings of convex polygons with congruent triangles},
Discrete Comput.\ Geom.\ \textbf{48} (2012), 330--372.

\bibitem{LaczkovichEll} M.~Laczkovich, \emph{Rational points of some elliptic curves related to
the tilings of the equilateral triangle}, Discrete Comput.\ Geom.\ \textbf{64} (2020), 985--994.

\bibitem{SWW} S.~L.~Snover, C.~Waiveris and J.~K.~Williams, \emph{Rep-tiling for triangles},
Discrete Math.\ \textbf{91} (1991), 193--200.

\bibitem{Soifer} A.~Soifer, \emph{How does one cut a triangle?}, 2nd ed., Springer, 2009.

\end{thebibliography}

\end{document}
